### 2020-09-10 ms.tex
init

\documentclass[journal]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{datatool}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{positioning}

\newcommand{\DTLfetchsave}[5]{
	\edtlgetrowforvalue{#2}{\dtlcolumnindex{#2}{#3}}{#4}
	\dtlgetentryfromcurrentrow{\dtlcurrentvalue}{\dtlcolumnindex{#2}{#5}}
	\let#1\dtlcurrentvalue}

\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}

\begin{document}
\DTLloaddb{keys_values}{results/keys-values.csv}

\title{Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT scans}
\author{Paschalis~Bizopoulos, Nicholas~Vretos and Petros~Daras, Senior Member, IEEE
\thanks{P. Bizopoulos, N. Vretos and P. Daras are with the Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: \{pbizopoulos,vretos,daras\}@iti.gr}}

\maketitle

\begin{abstract}
	Recently there has been an explosion in the use of Deep Learning (DL) methods for medical image segmentation.
	However the field's reliability is hindered by the lack of a common base of reference for accuracy/performance evaluation and the fact that previous research uses different datasets for evaluation.
	In this paper, an extensive comparison of DL models for lung and COVID-19 lesion segmentation in Computerized Tomography (CT) scans is presented, which can also be used as a benchmark for testing medical image segmentation models.
	Four DL architectures (Unet, Linknet, FPN, PSPNet) are combined with $25$ randomly initialized and pretrained encoders (variations of VGG, DenseNet, ResNet, ResNext, DPN, MobileNet, Xception, Inception-v4, EfficientNet), to construct $200$ tested models.
	Three experimental setups are conducted for lung segmentation, lesion segmentation and lesion segmentation using the original lung masks.
	A public COVID-19 dataset with $100$ CT scan images ($80$ for train, $20$ for validation) is used for training/validation and a different public dataset consisting of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes for testing.
	Multiple findings are provided including the best architecture-encoder models for each experiment as well as mean Dice results for each experiment, architecture and encoder independently.
	Finally, the upper bounds improvements when using lung masks as a preprocessing step or when using pretrained models are quantified.
	The source code and $600$ pretrained models for the three experiments are provided, suitable for fine-tuning in experimental setups without GPU capabilities.
\end{abstract}

\begin{IEEEkeywords}
	COVID 19, deep learning, lung segmentation, lesion segmentation
\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}
Coronavirus Disease 2019 (COVID-19) has emerged in December of 2019 and was declared as a pandemic in March of 2020~\cite{world2020coronavirus}.
The Severe Acute Respiratory Syndrome Coronavirus 2 (SARS-CoV-2) has certain properties that makes it highly infectious, thus, turning ineffective government policy measures such as social distancing and increasing the need for fast and accurate diagnosis of the disease.
A well established, high resolution, imaging procedure that targets lungs and depicts rich pathological information is Computerized Tomography (CT) scan.
More specifically, for a COVID-19 patient, CT scan images show bilateral patchy shadows or ground glass opacity on the infected region~\cite{wang2020clinical}, which are not always visible in common X-Ray scans~\cite{ng2020imaging}.
Another method that has been used for COVID-19 diagnosis is the so-called Reverse-Transcription Polymerase Chain Reaction (RT-PCR), which, however, has been found to have lower sensitivity compared to CT~\cite{ai2020correlation} scan and is more time consuming.

Medical experts often need to examine a large number of CT scan images, which is an error prone and time consuming process.
To that aim, automatic segmentation methods are being proposed that segment regions-of-interest (ROIs) of different size and shape such as lungs, nodules and lesions, taking advantage of the CT scan resolution.
These methods facilitate medical experts in diagnosing by focusing on the ROIs instead of the whole image.
Methods for automatic segmentation in the lung area from the literature include the use of morphological operations~\cite{hu2001automatic}, active contours~\cite{keshani2013lung} and fuzzy clustering~\cite{manikandan2016lung}.

Feature engineering methods however, were surpassed by end-to-end learning such as Deep Learning (DL)~\cite{lecun2015deep}, which were successfully applied in medical image segmentation tasks~\cite{minaee2020image}.
More specifically, applications of DL methods in medical image segmentation primarily target lungs~\cite{skourt2018lung, jin2020ai}, pathological lungs~\cite{harrison2017progressive}, infections~\cite{fan2020inf, chen2020residual, wang2020noise}, lungs and infections~\cite{yan2020covid}, lungs and COVID-19 lesions~\cite{shan2020lung}.
The majority of them uses encoder-decoder architectures such as Unet~\cite{ronneberger2015u} and its variations.

A major issue in the field of lung/lesion segmentation (and medical image segmentation in general) is the use of different datasets for evaluating newly proposed models.
Moreover, there is lack of benchmark baseline models that could play the role of reference for evaluating the accuracy and the performance of proposed models.
Benchmarks for COVID-19 in CT scan images were provided in the literature, such as Ma et al.~\cite{ma2020towards} that has a limited number of cases and He et al.~\cite{he2020benchmarking} that test $20$ models for lung segmentation of COVID-19 patients.
Other comparison studies on similar tasks such as lung nodule segmentation were proposed in~\cite{kalpathy2016comparison}, which compare three non-learnable algorithms, where each one is created by a different research group.
Comparison studies of deep learning image segmentation tasks has also been conducted on non-medical images such as coral reef images~\cite{king2018comparison} where the authors test four models as well as aerial city images~\cite{liu2018comparison} where the authors test $12$ different models.
No previous work, to the best of our knowledge, includes a comprehensive quantified comparison of $600$ DL models on the task of image segmentation.

In this paper, four of the most widely used DL image segmentation architectures are explored, namely Unet~\cite{ronneberger2015u}, Linknet~\cite{chaurasia2017linknet}, Feature Pyramid Network (FPN)~\cite{lin2017feature} and Pyramid Scene Parsing Network (PSPNet)~\cite{zhao2017pyramid} combined with $25$ encoders for lung and COVID-19 lesion segmentation in CT scan images.
The contribution of this paper in the field of medical image segmentation can be summarized as follows:
\begin{itemize}
	\item derivation of best architecture-encoder combinations for the three experiments that are conducted (lung, lesion and lesion with lung masks experiments),
	\item quantitative comparison of architectures,
	\item quantitative comparison of encoders,
	\item quantitative comparison of lesion segmentation with and without masks (in this case lungs) as a preprocessing step,
	\item quantitative comparison of random and ImageNet initialization,
	\item open source implementation\footnote{\url{https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct}},
	\item release of $600$ pretrained models of all experimental setups for use by external researchers.
\end{itemize}

The rest of the paper is organized as follows: a detailed description of the models and their components (architecture, encoder) is provided in Section~\ref{sec:methods}, the datasets used are presented in Section~\ref{sec:datasets}, the experimental setup used to evaluate the models is shown in Section~\ref{sec:experimentalsetup} and the results are demonstrated in Section~\ref{sec:results}. Finally the findings in relation with findings in the previous literature are shown in Section~\ref{sec:discussion} and the final remarks are concluded in Section~\ref{sec:conclusions}.

\section{Methods}
In this Section the problem of segmentation is formalized and the architectures and encoders that are used in this study are presented.

\label{sec:methods}
\subsection{Formalization}
Let $\mathcal{D}$ be a dataset containing images $\bm{X} \in \mathbb{R}^{n_r, n_c}$ and $\bm{Y} \in \{0, 1\}^{n_r, n_c}$ the corresponding target mask (in our case $n_r=512$, $n_c=512$).
Let $m_{ex, ar, en, ew}$ be a DL model for segmentation where $ex$ denotes the specific experiment, $ar$ the architecture, $en$ the encoder and $ew$ the encoder weights.
The `encoder' is defined as the part of the model that performs the feature extraction.
The model $m_{ex, ar, en, ew}$ is trained on a dataset $\mathcal{D}_{train}\subset\mathcal{D}$ consisting of $\bm{X}_{train} \in \mathbb{R}^{n_r, n_c}$ and $\bm{Y}_{train} \in \{0, 1\}^{n_r, n_c}$.
Moreover a validation dataset is defined as $\mathcal{D}_{val}\subset\mathcal{D}$ where $\mathcal{D}_{val}\cap\mathcal{D}_{train}=\emptyset$ consisting of $\bm{X}_{val} \in \mathbb{R}^{n_r, n_c}$ and $\bm{Y}_{val} \in \{0, 1\}^{n_r, n_c}$.
Therefore, the objective of the experiments conducted in this study can be designed as, finding an optimal point in the parameter space of $m_{ex, ar, en, ew}$ during training such that when presented with an input from $\mathcal{D}$ such as $\bm{X}_{val}$, its prediction $\hat{\bm{Y}}_{val} \in [0, 1]^{n_r, n_c}$ is as near as possible with the target $\bm{Y}_{val}$.
This is implemented by selecting the model that performs the minimum validation error out of all epochs.
Subsequently, the selected models are tested on the generalization ability on an unseen $\mathcal{D}_{test}$ with $\mathcal{D}_{test}\cap\mathcal{D}=\emptyset$.
A high level overview of the training of the models can be seen in Fig.~\ref{fig:highleveloverview}.

\begin{figure}[!t]
	\centering
	\begin{tikzpicture}[]
		\node[] (input) {\includegraphics[scale=0.3]{results/lesion-segmentation-a-image}};
		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{results/lesion-segmentation-a-prediction-train-masked-image}};
		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{results/lesion-segmentation-a-mask-train-masked-image}};
		\node[] at (0, 1){$\bm{X}$};
		\node[] at (5.2, 1){$\hat{\bm{Y}}$};
		\node[] at (5.2, -4){$\bm{Y}$};
		\draw[->] (input) -- node{} (architecture);
		\draw[->] (architecture) -- node{} (output);
		\draw[->] (output) -- node{} (loss);
		\draw[->] (mask) -- node{} (loss);
		\draw[->] (loss) -| node[shift={(0, -0.2)}]{backpropagation} (architecture);
	\end{tikzpicture}
	\caption{High level overview of a lesion segmentation model with an architecture consisting of an encoder trained using a single training augmented image.
	$\bm{X}$ is the input, $\bm{Y}$ is the target mask, $\hat{\bm{Y}}$ is the predicted mask and $\mathcal{L}$ is the loss function, which in this case is the Dice loss.
	Green and red pixels at $\hat{\bm{Y}}$ depict correctly and falsely classified pixels, while green pixels at $\bm{Y}$ depict the pixels of the target mask.
	Arrows denote the flow of the feed-forward and backpropagation pass.
	$\bm{X}$ is passed to the architecture consisting of a specific encoder and $\hat{\bm{Y}}$ is calculated.
	Then $\hat{\bm{Y}}$ and $\bm{Y}$ are used to calculate the loss, which is then used to backpropagate the error to the weights.
	This procedure is repeated for a number of times using more training examples till $\mathcal{L}$ converges.}
	\label{fig:highleveloverview}
\end{figure}

\subsection{Architectures}
\label{sec:architectures}
Four architectures are used as the basis of the models to be tested:
\begin{itemize}
	\item Unet~\cite{ronneberger2015u}
	\item Linknet~\cite{chaurasia2017linknet}
	\item Feature Pyramid Network (FPN)~\cite{lin2017feature}
	\item Pyramid Scene Parsing Network (PSPNet)~\cite{zhao2017pyramid}
\end{itemize}

Unet~\cite{ronneberger2015u} combines an encoder that scales down the features to a lower dimensional bottleneck and a decoder that scales them up to original dimensions.
It also uses skip connections that were proven to improve image segmentation results~\cite{drozdzal2016importance}.
Linknet~\cite{chaurasia2017linknet} is similar to Unet with the difference of using residual~\cite{he2016deep} instead of convolutional blocks in its encoder and decoder networks.
Feature Pyramid Network (FPN)~\cite{lin2017feature} is also similar to Unet with the difference of applying a $1\times1$ convolution layer and adding the features instead of copying and appending them as done in the Unet architecture.
The Pyramid Scene Parsing Network (PSPNet)~\cite{zhao2017pyramid} exploits a pyramid pooling module to aggregate the image global context information with an auxiliary loss~\cite{hu2019comparison}.

\subsection{Encoders}
\label{sec:encoders}
The following encoders are used along with their variations denoted in the parenthesis:
\begin{itemize}
	\item VGG~\cite{simonyan2014very} (11, 13, 19)
	\item DenseNet~\cite{huang2017densely} (121, 161, 169, 201)
	\item ResNet~\cite{he2016deep} (18, 34, 50, 101, 152)
	\item ResNext~\cite{xie2017aggregated}
	\item Dual Path Networks (DPN)~\cite{chen2017dual} (68, 98)
	\item MobileNet~\cite{howard2017mobilenets}
	\item Xception~\cite{chollet2017xception}
	\item Inception-v4~\cite{szegedy2017inception}
	\item EfficientNet~\cite{tan2019efficientnet} (b0, b1, b3, b4, b5, b6)
\end{itemize}

VGG~\cite{simonyan2014very} is named after the Visual Geometry Group that proposed it and took the second place during the ImageNet Competition in 2014~\cite{deng2009imagenet}.
It was one of the first models that demonstrated the importance of depth in DL and it is preferred for tasks such as feature extraction due to its simple repeating structure.
On the other hand, ResNet's~\cite{he2016deep} (abbreviation of Residual Networks) contributions allowed training deep networks by using layers that learn residual functions with reference to layer inputs, while DenseNet~\cite{huang2017densely} uses connections between each layer and every other layer in a feed-forward fashion.
Moreover ResNext~\cite{xie2017aggregated} consists of a stack of residual blocks, which are subject to two rules.
The first one is that layers that output spatial maps with the same size, share hyper-parameters and the second is that when a spatial map is downsampled by two, the width of the blocks is multiplied by two.
Dual Path Networks (DPN)~\cite{chen2017dual} proposed as a network that combines feature re-usage and feature exploration that ResNet and DenseNet do respectively, while MobileNet~\cite{howard2017mobilenets} constructed to fill the need of training and inferencing on devices with low computational capabilities such as embedded device and mobile phones.
Xception~\cite{chollet2017xception} is a variation of Inception Network~\cite{szegedy2015going} in which the inception modules have been replaced with depthwise convolutions followed by a pointwise convolution.
Finally Inception-v4~\cite{szegedy2017inception} combines previous inception architectures with residual connections achieving state-of-the-art performance on the ImageNet, while EfficientNet~\cite{tan2019efficientnet} is an improvement of MobileNet where the compound scaling module was proposed as an efficient way to uniformly scale depth, width and resolution.

\section{Datasets}
\label{sec:datasets}
Two public COVID-19 CT scan datasets with lung and lesion masks were used.
The first dataset\footnote{\url{http://medicalsegmentation.com/covid19/}} consists of $100$ CT axial scans from $<40$ patients with $512\times 512$ size and corresponding lung masks from~\cite{hofmanninger2020automatic} and lesion masks labeled with four classes (none, ground-glass, consolidation, pleural effusion).
The original dataset, without the annotations, was selected from the Italian Society of Medical and Interventional Radiology\footnote{\url{https://www.sirm.org/category/senza-categoria/covid-19/}}.
The second dataset\footnote{\url{https://radiopaedia.org/articles/covid-19-3}} consists of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes (a set of CT scan images acquired from the same patient at the same moment) with corresponding target masks.
373 out of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ were annotated as positive and segmented by a radiologist by the same group as the first dataset.
Raw data from both datasets contain samples in Hounsfield units~\cite{schneider1996calibration}.

Regarding preprocessing, first the positive classes of the pixels of the images in the first dataset are merged into one, converting the problem to a binary segmentation problem.
The CT scan images from the second dataset are resized to $512\times 512$, and both datasets are normalized with $\mu=-500$ and $\sigma=500$.
We use $80$ scans from the first dataset for training the models, $20$ scans for validation and all scans from the second dataset for the testing of the models.

In Fig.~\ref{fig:hist} the histograms of the pixel intensities of all the CT scan images and the target masks in the test dataset after normalization, for each of the three experiments, are depicted.
The considerable overlap between the histograms makes the use of thresholding models in this kind of problem unsuitable, thus justifying the use of learning models such as DL.

\begin{figure*}[!t]
	\rotatebox[origin=l]{90}{\hspace{4em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{results/lung-segmentation-hist}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{results/lesion-segmentation-a-hist}}
	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{results/lesion-segmentation-b-hist}}
	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
	The vertical axis depicts the normalized frequencies of each pixel intensity in the logarithmic scale.
	The outlier bar at zero is because most of the pixels in the target masks are near zero.}
	\label{fig:hist}
\end{figure*}

\section{Experimental setup}
\label{sec:experimentalsetup}
In this Section the experimental setup is presented.
In total three experiments are conducted:
\begin{itemize}
	\item lung segmentation
	\item lesion segmentation (referred to as `lesion segmentation A')
	\item lesion segmentation with lung masks (referred to as `lesion segmentation B')
\end{itemize}

The choice of these experiments covers balanced (lung segmentation), unbalanced (lesion segmentation A) and unbalanced with preprocessing (lesion segmentation B) image segmentation tasks and the findings could apply in image segmentation tasks with non-medical images.
Each of the performed experiments uses a different target mask $\bm{Y}$, where for the `lesion segmentation B' the corresponding lung masks is also applied in the input image $\bm{X}$.

Each model is constructed using a unique combination of the four architectures described in subsection~\ref{sec:architectures} and the $25$ encoders referenced in subsection~\ref{sec:encoders}.
The selection of architectures and encoders was based on the restriction of the GPU memory of our graphics card, combined with the value of batch size.
Then, for each model we also test the randomly initialized and its ImageNet pretrained version.

The default values for every hyperparameter of the models were used (as seen in Table.~\ref{table:architecturehyperparameters}), to avoid favoring models that were proposed after being evaluated in a controlled experimental setup.
The activation function for all architectures was sigmoid that squashes the output in the range of $[0, 1]$.

\begin{table}[]
	\centering
	\caption{Architecture hyperparameters}
	\label{table:architecturehyperparameters}
	\begin{tabular}{l|c|c|c}
		\toprule
		\textbf{Architecture} & \textbf{\makecell{Encoder\\ depth}}          & \textbf{Batch Norm}                & \textbf{Various}                                                                                             \\ \hline
		Unet    & 5 & Yes (decoder) & \makecell{decoder channel sizes =\\ (256, 128, 64, 32, 16)}                                 \\ \hline
		Linknet & 5 & Yes (decoder) & -                                                                              \\ \hline
		FPN     & 5 & No            & \makecell{pyramid channels=256,\\ segment channels=128,\\ merge policy=add,\\ dropout=0.2} \\ \hline
		PSPNet  & 3 & Yes (encoder) & \makecell{output channels=512,\\ dropout=0.2}                                              \\ \hline
	\end{tabular}
\end{table}

For all experiments and in each epoch during training, data augmentation is applied on the images from the training dataset:
\begin{itemize}
	\item horizontal/vertical flip each with probability 50\%,
	\item rotation with an angle chosen from a uniform distribution with range $[-180^{\circ}, 180^{\circ}]$ and
	\item scale within a range of $[0.5, 1.5]$ with zero padding
\end{itemize}

During training the Soft Dice Loss is used to calculate the error of the model on the training dataset as:
\begin{equation}
	Soft Dice Loss = 1 - 2\frac{\sum\limits^{n_r}_i\sum\limits^{n_c}_j\bm{Y}_{ij}\hat{\bm{Y}}_{ij}}{\sum\limits^{n_r}_i\sum\limits^{n_c}_j\bm{Y}_{ij}^2 + \sum\limits^{n_r}_i\sum\limits^{n_c}_j\hat{\bm{Y}}_{ij}^2 + \epsilon},
\end{equation}

where $\bm{Y}_{ij}$, $\hat{\bm{Y}}_{ij}$ are the pixel intensities at the $i^{th}$ column, $j^{th}$ row of the target mask and predicted mask, respectively (which applies for $\bm{Y}_{train}$, $\bm{Y}_{val}$ and $\bm{Y}_{test}$) and $\epsilon=10^{-5}$.
The model selection is done using Soft Dice Loss in each epoch during training on the validation dataset.
During testing, the predicted mask $\hat{\bm{Y}}_{test}$ is binarized with a threshold value of $0.5$ allowing us to use hard metrics for testing the models:
\begin{equation}
	Sensitivity = \frac{TP}{TP + FN + \epsilon}
\end{equation}
\begin{equation}
	Specificity = \frac{TN}{TN + FP + \epsilon}
\end{equation}
\begin{equation}
	Dice = \frac{2TP}{2TP + FP + FN + \epsilon}
\end{equation}

where $TP$, $TN$, $FP$ and $FN$ are the true positive, true negative, false positive and false negative of $\hat{\bm{Y}}$ w.r.t $\bm{Y}$, respectively and $\epsilon=10^{-5}$ to prevent division with zero.
When $TP+FP=0$ the model has correctly identified that the input does not have any positive pixel and in that case all metrics are set to $1$.

We train a total of $600$ different models for the three experiments each one for $\DTLfetch{keys_values}{key}{num_epochs}{value}$ epochs with a batch size of $\DTLfetch{keys_values}{key}{batch_size}{value}$, which was the maximum possible considering the GPU memory restriction.
We use the optimizer~\cite{kingma2014adam} with the default values of learning rate $0.001$, $\beta_1=0.9$, $\beta_2=0.999$, $\epsilon=10^{-8}$, without weight decay.
Pytorch~\cite{paszke2019pytorch} and the `Segmentation Models Pytorch' library~\cite{yakubovskiy2019segmentation} were used for implementing the experiments, a GeForce RTX 2080 Ti Graphics Card with 11Gb RAM from NVIDIA and an Intel Core i9-9900K CPU @3.60GHz, on a Linux-based operating system for training the models for two weeks.
A pseudo-code implementation of the experimental setup is shown in Algorithm~\ref{alg:experimentalsetup}.

\begin{algorithm}[H]
	\caption{Experimental setup}
	\label{alg:experimentalsetup}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE $epochs$
		\ENSURE $metrics$
		\\ \textit{Hyperparameters:  $\lambda$, $batches$}
		\FOR {$ex$ = 1 to $n_{experiments}$}
		\FOR {$ar$ = 1 to $n_{architectures}$}
		\FOR {$en$ = 1 to $n_{encoders}$}
		\FOR {$ew$ = 1 to $n_{encoder\ weights}$}
		\FOR {$ep$ = 1 to $epochs$}
		\FOR {$b$ = 1 to $batches$}
		\STATE $\bm{Y}_{train}, \bm{X}_{train} \sim \mathcal{D}_{train}$
		\STATE $\bm{Y}_{train}, \bm{X}_{train} \leftarrow Augm(\bm{Y}_{train}, \bm{X}_{train})$
		\STATE $\hat{\bm{Y}}_{train} \leftarrow m_{ex, ar, en, ew}(\bm{X}_{train})$
		\STATE $\mathcal{L}_{train} \leftarrow DiceLoss(\hat{\bm{Y}}_{train}, \bm{Y}_{train})$
		\STATE $\nabla\mathcal{L}_{train} = \left( \frac{\partial\mathcal{L}}{\partial\bm{w}^{(1)}},\ldots\frac{\partial\mathcal{L}}{\partial\bm{w}^{(q)}}\right)$
		\STATE $\Delta\bm{w}^{(i)} \leftarrow -\lambda\frac{\partial\mathcal{L}}{\partial\bm{w}^{(i)}}$
		\ENDFOR
		\FOR {$b$ = 1 to $batches$}
		\STATE $\bm{Y}_{val}, \bm{X}_{val} \sim \mathcal{D}_{val}$
		\STATE $\hat{\bm{Y}}_{val} \leftarrow m_{ex, ar, en, ew}(\bm{X}_{val})$
		\STATE $\mathcal{L}_{val} \leftarrow DiceLoss(\hat{\bm{Y}}_{val}, \bm{Y}_{val})$
		\ENDFOR
		\IF{$\mathcal{L}_{val} < \mathcal{L}_{val}^{best}$}
		\STATE $m_{ex, ar, en, ew}^{best} \leftarrow m_{ex, ar, en, ew}$
		\ENDIF
		\ENDFOR
		\STATE $\hat{\bm{Y}}_{test} \leftarrow m_{ex, ar, en, ew}^{best}(\bm{X}_{test})$
		\STATE $metrics_{ex, ar, en, ew} = metrics(\hat{\bm{Y}}_{test}, \bm{Y}_{test})$
		\ENDFOR
		\ENDFOR
		\ENDFOR
		\ENDFOR
		\RETURN $metrics$
	\end{algorithmic}
\end{algorithm}

\section{Results}
\label{sec:results}
In this Section the results of the three experimental setups are demonstrated, along with several comparisons between experiments, architectures, encoders and weight initialization schemes.

\subsection{Overall}
In Table.~\ref{table:metrics} the resulted metrics of all experiments are presented.
The best combination of architecture-encoder for each combination of encoder weight initialization, experimental setup and metric are showin in bold.
The mean Dice results for each experiment are $\DTLfetch{keys_values}{key}{lung-segmentation-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-imagenet-std}{value}\%$, for `lesion segmentation A' and $\DTLfetch{keys_values}{key}{lesion-segmentation-b-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-imagenet-std}{value}\%$, for `lesion segmentation B'.
The best performing models w.r.t.\ Dice for each experiment were the \DTLfetch{keys_values}{key}{lung-segmentation-architecture-imagenet-index-max}{value}-\DTLfetch{keys_values}{key}{lung-segmentation-encoder-imagenet-index-max}{value} ($\DTLfetch{keys_values}{key}{lung-segmentation-imagenet-max}{value}\%$) for lung segmentation, \DTLfetch{keys_values}{key}{lesion-segmentation-a-architecture-imagenet-index-max}{value}-\DTLfetch{keys_values}{key}{lesion-segmentation-a-encoder-imagenet-index-max}{value} ($\DTLfetch{keys_values}{key}{lesion-segmentation-a-imagenet-max}{value}\%$) for lesion segmentation A and \DTLfetch{keys_values}{key}{lesion-segmentation-b-architecture-imagenet-index-max}{value}-\DTLfetch{keys_values}{key}{lesion-segmentation-b-encoder-imagenet-index-max}{value} ($\DTLfetch{keys_values}{key}{lesion-segmentation-b-imagenet-max}{value}\%$) for lesion segmentation B.
In Fig.~\ref{fig:predictedmasks} the predicted masks for $24$ out of the $600$ models are depicted, demonstrating the difference in segmentation quality between the best (\DTLfetch{keys_values}{key}{encoder-best}{value}) and the worst (\DTLfetch{keys_values}{key}{encoder-worst}{value}) performing encoder of the models for each architecture, with randomly initialized weights.
In Fig.~\ref{fig:dicevsnumparameters} the Dice vs.\ the number of parameters is plotted, demonstrating that there is positive correlation, suggesting that segmentation generally improves when using higher number of parameters.
However, this is not a significant positive correlation.
It is worth noting that the best model is not the one with the largest number of parameters.

\DTLfetchsave{\best}{keys_values}{key}{encoder-best}{value}
\DTLfetchsave{\worst}{keys_values}{key}{encoder-worst}{value}

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\hspace{1em}\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\hspace{1em}\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-FPN-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-PSPNet-\worst-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-FPN-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-PSPNet-\worst-masked-image}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation B}\subfloat[Unet]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\worst-masked-image}}
	\subfloat[Linknet]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\worst-masked-image}}
	\subfloat[FPN]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\worst-masked-image}}
	\subfloat[PSPNet]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\worst-masked-image}}
	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
	The three top columns correspond to predicted masks generated from a model with the best encoder and the bottom three for the worst.
	Rows correspond to each of the four architectures.
	Green and red depict correctly and falsely classified pixels respectively.}
	\label{fig:predictedmasks}
\end{figure}

\begin{figure}[!t]
	\rotatebox[origin=l]{90}{\hspace{4em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-scatter-dice-vs-num-parameters}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
	\\
	\rotatebox[origin=l]{90}{\hspace{4em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{results/diff-scatter-dice-vs-num-parameters}}
	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
	The green regions depict the kernel density estimate for all points using Gaussian kernels.
	The method used to calculate the estimator bandwidth was Scott and the points are assumed to be equally weighted.}
	\label{fig:dicevsnumparameters}
\end{figure}

\begin{table*}[!t]
	\centering
	\caption{Metrics}
	\label{table:metrics}
	\setlength\tabcolsep{6.5pt}
	\scalebox{0.64}{\input{results/metrics.tex}}
\end{table*}

\subsection{Architecture comparison}
In Fig.~\ref{fig:loss} the train and validation loss vs.\ epochs of the four architectures segregated upon encoders is depicted.
In all experiments and architectures, the training loss during the $5$ first epochs, decreases fast and in a slower rate during the next epochs.
We can observe the same behaviour for validation loss during the $15$ first epochs but with more variability, which can be explained by the use of the dice loss as a validation metric.
More specifically, we observe faster convergence for PSPNet for training loss compared to the other architectures, greater variance for FPN and lower convergence for Linknet in both training and validation.
In Fig.~\ref{fig:box} the Dice boxplots for the three experiments is plotted.
Regarding time performance for training and inference, the fastest architecture is PSPNet and the slowest is Linknet even having more parameters than Unet.

\begin{figure}[!t]
	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-validation-loss}}
	\\
	\rotatebox[origin=l]{90}{\hspace{1.2em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-validation-loss}}
	\\
	\rotatebox[origin=l]{90}{\hspace{1.8em}\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-loss}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\hspace{1.3em}\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-diff-loss}}
	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-diff-loss}}
	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
	Rows correspond to experimental setups and the difference between lesion segmentation B and A and columns correspond to train and validation losses.}
	\label{fig:loss}
\end{figure}

\begin{figure}[!t]
	\rotatebox[origin=l]{90}{\hspace{3.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-boxplot-dice}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-boxplot-dice}}
	\\
	\rotatebox[origin=l]{90}{\hspace{3.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-boxplot-dice}}
	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{results/initialization-boxplot-dice}}
	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}
	\label{fig:box}
\end{figure}

The mean Dice results for Unet are $\DTLfetch{keys_values}{key}{lung-segmentation-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-Unet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-Unet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-Unet-imagenet-std}{value}\%$ for `lesion segmentation B'.
The mean Dice results for Linknet are $\DTLfetch{keys_values}{key}{lung-segmentation-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-Linknet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-Linknet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-Linknet-imagenet-std}{value}\%$ for `lesion segmentation B'.
The mean Dice results for FPN are $\DTLfetch{keys_values}{key}{lung-segmentation-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-FPN-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-FPN-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-FPN-imagenet-std}{value}\%$ for `lesion segmentation B'.
The mean Dice results for PSPNet are $\DTLfetch{keys_values}{key}{lung-segmentation-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-PSPNet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation B'.

In Fig.~\ref{fig:volumes} the predictions as a volume for the three experiments, for the resnet18 encoder are visualized, demonstrating good match with the original masks.

\begin{figure*}[!t]
	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-mask--volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-Unet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-Linknet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-FPN-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-PSPNet-None-volume}}
	\\
	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-mask--volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-Unet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-Linknet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-FPN-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-PSPNet-None-volume}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-mask--volume}}
	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-Unet-None-volume}}
	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-Linknet-None-volume}}
	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-FPN-None-volume}}
	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-PSPNet-None-volume}}
	\caption{Reconstructed volumes from predicted masks.
	Reconstruction was done by stacking the predicted masks on the z-axis and then applying the marching cubes algorithm.}
	\label{fig:volumes}
\end{figure*}

\subsection{Lesion segmentation A vs.\ Lesion segmentation B}
In the bottom two subfigures in Fig.~\ref{fig:loss} the difference of the train and validation loss between the `lesion segmentation A' and `lesion segmentation B' are depicted.
We observe convergence between the losses, which is an indication that when training for large number of epochs the use of lung masks, as a preprocessing step, is less required.

\subsection{Random initialization vs.\ pretrained on ImageNet}
In Fig.~\ref{fig:weights} the weights are depicted, in which we observe that with random initialization the weights depict high and low frequency textures after training.
The Dice for using random initialization is $\DTLfetch{keys_values}{key}{None-mean}{value}\%\pm\DTLfetch{keys_values}{key}{None-std}{value}\%$ and for ImageNet initialization is $\DTLfetch{keys_values}{key}{imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{imagenet-std}{value}\%$.

\begin{figure}[!t]
	\rotatebox[origin=l]{90}{\hspace{2.8em}\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-before-weights}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-after-weights}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\hspace{2.8em}\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-before-weights}}
	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-after-weights}}
	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.
	The two left and two right grids correspond to random and ImageNet pretrained initialization, respectively.
	The data range of the colormap of the images has been adjusted in the range $[-0.4, 0.4]$.}
	\label{fig:weights}
\end{figure}

\section{Discussion}
\label{sec:discussion}
A motivation for this study is that the large amount of new models that are proposed, rarely conduct ablation studies and do not compare with simple baselines.
This study can be used as a set of baseline models that DL model designers will test on, to confirm and evaluate whether their novel model performs better than other models, e.g.\ by comparing their accuracy with models with the same number of parameters and/or training/validation time.

A common preprocessing step for lesion segmentation is using lung masks as either from manual annotation or from an automatic method.
This step naturally improves lesion segmentation since the model only needs to search within the lung region instead of the whole image.
Moreover, the use of this step is necessary in cases where the lesion is orders of magnitude smaller than the lungs and the background, justifying the characterization of lesion datasets as `unbalanced'.
The arguments against using this preprocessing step is that the complexity of the model and the cost of annotation by the experts are increased.
The question to be answered by the expert is whether it is beneficial to increase the model complexity and the annotation cost to achieve the additional lesion segmentation accuracy increase.
Related previous work was conducted by Shi et al.~\cite{shi2020review}, which categorized COVID-19 segmentation models between:
\begin{itemize}
	\item the lung-lesion-oriented models, which directly segment lesions and
	\item the lung-region-oriented models, which first segment the lungs and then pass the masked region for further segmentation or classification.
\end{itemize}

Regarding the encoder weight initialization experiment we confirm previous research such as~\cite{orsic2019defense} that pretrained weights significantly improve segmentation results, however we hypothesize that for as the number of epochs increases, the accuracy gap between them decreases.
Similar positive findings regarding transfer learning such as improved performance and faster convergence were also reported in~\cite{wang2020does}.

Limitations of this study include the use of small number of training data, however this is partially solved by the use of data augmentation methods that are applied on each training epoch.
Moreover, it is costly to gather and annotate medical images especially when extreme events such as the COVID-19 outbreak occur.
Therefore, the use of this study training dataset is representative of medical datasets that exist in the wild as summarized in~\cite{hesamian2019deep}, which contains samples in the order of $10^2$ to lower $10^3$.

Future work includes the use of neuron and layer attribution methods to investigate reasons that specific combinations of architectures and encoders perform better than others.

\section{Conclusions}
\label{sec:conclusions}
The need for fast, accurate and automatic diagnosis of COVID-19 requires highly reliable and publicly available models.
We demonstrate specific properties that increase model segmentation and help experts in improved diagnosis by publicly providing pretrained models ready to be used for fine-tuning in experimental setups without GPU.

\section*{ACKNOWLEDGMENT}
This work received funding from the European Union’s Horizon 2020 research and innovation programme under grant agreement No 875325 (TeNDER, affecTive basEd iNtegrateD carE for betteR Quality of Life).

\bibliographystyle{IEEEtran}
\bibliography{ms}

\end{document}

### 2020-09-10 datasets.py

@@ -1,0 +1,142 @@
+import gdown
+import glob
+import nibabel as nib
+import numpy as np
+import os
+import requests
+import torch
+
+from torch.utils.data import Dataset
+from zipfile import ZipFile
+from torchvision.transforms import functional as tf
+
+def preprocess(image, lung_mask, lesion_mask, use_transforms):
+    image = tf.to_pil_image(image.astype('float32'))
+    lesion_mask = tf.to_pil_image(lesion_mask.astype('uint8'))
+    lung_mask = tf.to_pil_image(lung_mask.astype('uint8'))
+    image = tf.resize(image, [512, 512])
+    lesion_mask = tf.resize(lesion_mask, [512, 512])
+    lung_mask = tf.resize(lung_mask, [512, 512])
+    if use_transforms:
+        if np.random.rand() > 0.5:
+            image = tf.hflip(image)
+            lesion_mask = tf.hflip(lesion_mask)
+            lung_mask = tf.hflip(lung_mask)
+        if np.random.rand() > 0.5:
+            image = tf.vflip(image)
+            lesion_mask = tf.vflip(lesion_mask)
+            lung_mask = tf.vflip(lung_mask)
+        scale = np.random.rand() + 0.5
+        rotation = 360 * np.random.rand() - 180
+        image = tf.affine(image, rotation, [0, 0], scale, 0)
+        lesion_mask = tf.affine(lesion_mask, rotation, [0, 0], scale, 0)
+        lung_mask = tf.affine(lung_mask, rotation, [0, 0], scale, 0)
+    image = tf.to_tensor(image)
+    lesion_mask = tf.to_tensor(lesion_mask)
+    lung_mask = tf.to_tensor(lung_mask)
+    image = tf.normalize(image, -500, 500)
+    lesion_mask = lesion_mask.bool()
+    lung_mask = lung_mask.bool()
+    return image, lung_mask, lesion_mask
+
+
+class MedicalSegmentation1(Dataset):
+    def __init__(self, cache_dir, index_range, use_transforms):
+        urls = ['https://drive.google.com/uc?id=1SJoMelgRqb0EuqlTuq6dxBWf2j9Kno8S', 'https://drive.google.com/uc?id=1MEqpbpwXjrLrH42DqDygWeSkDq0bi92f', 'https://drive.google.com/uc?id=1zj4N_KV0LBko1VSQ7FPZ38eaEGNU0K6-']
[…]

### 2020-09-10 hubconf.py

@@ -1,0 +1,27 @@
+dependencies = ['segmentation_models_pytorch']
+
+from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
+
+
+def segmentation_model(pretrained=True, experiment_name='lung-segmentation', architecture='Unet', encoder='resnet18', encoder_weights='imagenet'):
+    """
+    segmentation model
+    pretrained (bool): load pretrained weights into the model
+    experiment_name ('lung-segmentation', 'lesion-segmentation-a', 'lesion-segmentation-b'): Experiment name
+    architecture_name ('Unet', 'Linknet', 'FPN', 'PSPNet'): Architecture name
+    encoder ('vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6'): Encoder
+    encoder_weights (None, 'imagenet'): Encoder weights
+    """
+    if architecture_name == 'Unet':
+        architecture = Unet
+    if architecture_name == 'Linknet':
+        architecture = Linknet
+    if architecture_name == 'FPN':
+        architecture = FPN
+    if architecture_name == 'PSPNet':
+        architecture = PSPNet
+    model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
+    if pretrained:
+        checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture.__name__}-{encoder}-{endocer_weights}.pt'
+        model.load_state_dict(torch.hub.load_state_dict_from_url(checkpoint, progress=False, map_location='cpu'))
+    return model

### 2020-09-10 losses.py

@@ -1,0 +1,27 @@
+eps = 1e-6
+
+def dice_loss(prediction, mask):
+    tp = (mask * prediction).sum([1, 2, 3])
+    fp = (mask * (1 - prediction)).sum([1, 2, 3])
+    fn = (~mask * prediction).sum([1, 2, 3])
+    is_mask_and_prediction_empty = (tp + fp) == 0
+    dice_loss_ = 1 - 2*tp / (2*tp + fp + fn + eps)
+    dice_loss_ *= ~is_mask_and_prediction_empty
+    return dice_loss_.mean()
+
+def metrics(prediction, mask):
+    prediction = prediction > 0.5
+    tp = (mask * prediction).sum().float()
+    tn = (~mask * ~prediction).sum().float()
+    fp = (mask * ~prediction).sum().float()
+    fn = (~mask * prediction).sum().float()
+    is_mask_and_prediction_empty = (tp + fp) == 0
+    if is_mask_and_prediction_empty:
+        specificity = 1
+        sensitivity = 1
+        dice = 1
+    else:
+        specificity = (tn / (tn + fp + eps)).item()
+        sensitivity = (tp / (tp + fn + eps)).item()
+        dice = (2*tp / (2*tp + fp + fn + eps)).item()
+    return sensitivity, specificity, dice

### 2020-09-10 main.py

@@ -1,0 +1,310 @@
+import argparse
+import itertools
+import numpy as np
+import pandas as pd
+import torch
+
+from torch import optim
+from torch.utils.data import DataLoader
+
+from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
+
+from datasets import MedicalSegmentation1, MedicalSegmentation2, CTSegBenchmark
+from losses import dice_loss, metrics
+from utilities import save_weights, save_hist, save_loss, save_scatter, save_architecture_box, save_initialization_box, save_3d, save_image, save_masked_image, get_num_parameters
+
+
+if __name__ == '__main__':
+    # DO NOT EDIT BLOCK
+    np.random.seed(0)
+    torch.backends.cudnn.benchmark = False
+    torch.backends.cudnn.deterministic = True
+    torch.cuda.manual_seed_all(0)
+    torch.manual_seed(0)
+
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--full', default=False, action='store_true')
+    args = parser.parse_args()
+
+    cache_dir = 'cache'
+    results_dir = 'results'
+    # END OF DO NOT EDIT BLOCK
+
+    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+    if args.full:
+        num_epochs = 100
+        index_train_range = range(80)
+        index_validation_range = range(80, 100)
+        index_test_volume_range = range(9)
+        encoder_list = ['vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6']
+    else:
+        num_epochs = 2
+        index_train_range = range(1)
+        index_validation_range = range(2, 4)
+        index_test_volume_range = range(1)
+        encoder_list = ['vgg11', 'resnet18', 'mobilenet_v2', 'efficientnet-b0']
+    batch_size = 2
+    architecture_list = [Unet, Linknet, FPN, PSPNet]
+    architecture_name_list = [architecture.__name__ for architecture in architecture_list]
[…]

### 2020-09-10 utilities.py

@@ -1,0 +1,176 @@
+import numpy as np
+
+from matplotlib import gridspec
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from mpl_toolkits.mplot3d import Axes3D
+from scipy.stats import gaussian_kde
+from skimage.measure import marching_cubes
+
+plt.rcParams['image.interpolation'] = 'none'
+plt.rcParams['savefig.format'] = 'pdf'
+plt.rcParams['savefig.bbox'] = 'tight'
+
+
+def save_weights(model, experiment_name, architecture_name, encoder_weights, results_dir):
+    rows = 8
+    columns = 8
+    fig = plt.figure(figsize=(4, 4.6))
+    gs = gridspec.GridSpec(rows, columns, wspace=0.0, hspace=0.0, left=0)
+    for index_rows in range(rows):
+        for index_columns in range(columns):
+            weight = list(model.children())[0].conv1.weight[index_rows*rows+index_columns]
+            ax = plt.subplot(gs[index_rows, index_columns])
+            plt.imshow(weight[0].detach().cpu().numpy(), cmap='gray', vmin=-0.4, vmax=0.4)
+            ax.set_xticklabels([])
+            ax.set_yticklabels([])
+    plt.savefig(f'{results_dir}/{experiment_name}-{architecture_name}-{encoder_weights}-weights')
+    plt.close()
+
+def save_hist(hist_images, hist_masks, hist_range, experiment_name, results_dir):
+    t = np.linspace(hist_range[0], hist_range[1], hist_masks.shape[-1])
+    hist_images = hist_images.reshape(-1, hist_images.shape[-1]).sum(0)
+    hist_masks = hist_masks.reshape(-1, hist_masks.shape[-1]).sum(0)
+    hist_maxes = max([hist_images.max(), hist_masks.max()])
+    hist_images /= hist_maxes
+    hist_masks /= hist_maxes
+    fig, ax = plt.subplots()
+    plt.bar(t, hist_images, width=t[1]-t[0], align='center', label='Images')
+    plt.bar(t, hist_masks, width=t[1]-t[0], align='center', label='Masks')
+    plt.xlabel('Normalized values', fontsize=15)
+    plt.xlim(hist_range)
+    plt.ylim([10**(-7), 1])
+    plt.grid(True, which='both')
+    ax.set_yscale('log')
+    ax.legend()
[…]

### 2020-09-10 web-app/main.py

@@ -1,0 +1,73 @@
+import gradio
+import torch
+
+from matplotlib import pyplot as plt
+from torchvision.transforms import functional as tf
+
+from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
+
+
+experiment_list = ['Lung segmentation', 'Lesion segmentation A']
+experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
+architecture_list = [Unet, Linknet, FPN, PSPNet]
+architecture_name_list = [architecture.__name__ for architecture in architecture_list]
+encoder_list = ['vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6']
+encoder_weights_list = ['None', 'imagenet']
+
+def preprocess(image):
+    if image.shape[0] in [1, 3]:
+        image = image[0]
+    elif image.shape[-1] in [1, 3]:
+        image = image[..., -1]
+    image = tf.to_pil_image(image)
+    image = tf.resize(image, [512, 512])
+    image = tf.to_tensor(image)
+    image = tf.normalize(image, image.mean(), image.std())
+    return image.unsqueeze(0)
+
+
+def predict(image, experiment_name, architecture_name, encoder, encoder_weights):
+    model_path = f'../results/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
+    if architecture_name == 'Unet':
+        architecture = Unet
+    if architecture_name == 'Linknet':
+        architecture = Linknet
+    if architecture_name == 'FPN':
+        architecture = FPN
+    if architecture_name == 'PSPNet':
+        architecture = PSPNet
+    model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
+    model.load_state_dict(torch.load(model_path, map_location=torch.device('cpu')))
+    model.eval()
+    image = preprocess(image)
+    prediction = model(image)
+    prediction = prediction[0, 0].detach().numpy()
[…]

### 2020-09-10 hubconf.py
fix

@@ -7,7 +7,7 @@ def segmentation_model(pretrained=True, experiment_name='lung-segmentation', arc
     """
     segmentation model
     pretrained (bool): load pretrained weights into the model
-    experiment_name ('lung-segmentation', 'lesion-segmentation-a', 'lesion-segmentation-b'): Experiment name
+    experiment_name ('lung-segmentation', 'lesion-segmentation-a'): Experiment name
     architecture_name ('Unet', 'Linknet', 'FPN', 'PSPNet'): Architecture name
     encoder ('vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6'): Encoder
     encoder_weights (None, 'imagenet'): Encoder weights
@@ -22,6 +22,6 @@ def segmentation_model(pretrained=True, experiment_name='lung-segmentation', arc
         architecture = PSPNet
     model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
     if pretrained:
-        checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture.__name__}-{encoder}-{endocer_weights}.pt'
+        checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture_name}-{encoder}-{endocer_weights}.pt'
         model.load_state_dict(torch.hub.load_state_dict_from_url(checkpoint, progress=False, map_location='cpu'))
     return model

### 2020-09-10 web-app/main.py

@@ -27,7 +27,6 @@ def preprocess(image):
 
 
 def predict(image, experiment_name, architecture_name, encoder, encoder_weights):
-    model_path = f'../results/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
     if architecture_name == 'Unet':
         architecture = Unet
     if architecture_name == 'Linknet':
@@ -37,7 +36,8 @@ def predict(image, experiment_name, architecture_name, encoder, encoder_weights)
     if architecture_name == 'PSPNet':
         architecture = PSPNet
     model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
-    model.load_state_dict(torch.load(model_path, map_location=torch.device('cpu')))
+    checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture_name}-{encoder}-{endocer_weights}.pt'
+    model.load_state_dict(torch.hub.load_state_dict_from_url(checkpoint, progress=False, map_location='cpu'))
     model.eval()
     image = preprocess(image)
     prediction = model(image)

### 2020-09-10 web-app/main.py
fix hubconf and web-app

@@ -36,7 +36,7 @@ def predict(image, experiment_name, architecture_name, encoder, encoder_weights)
     if architecture_name == 'PSPNet':
         architecture = PSPNet
     model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
-    checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture_name}-{encoder}-{endocer_weights}.pt'
+    checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/latest/download/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
     model.load_state_dict(torch.hub.load_state_dict_from_url(checkpoint, progress=False, map_location='cpu'))
     model.eval()
     image = preprocess(image)

### 2020-09-10 hubconf.py
fix hubconf

@@ -3,7 +3,7 @@ dependencies = ['segmentation_models_pytorch']
 from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
 
 
-def segmentation_model(pretrained=True, experiment_name='lung-segmentation', architecture='Unet', encoder='resnet18', encoder_weights='imagenet'):
+def segmentation_model(pretrained=True, experiment_name='lung-segmentation', architecture_name='Unet', encoder='resnet18', encoder_weights='imagenet'):
     """
     segmentation model
     pretrained (bool): load pretrained weights into the model

### 2020-09-10 hubconf.py
spelling mistake

@@ -22,6 +22,6 @@ def segmentation_model(pretrained=True, experiment_name='lung-segmentation', arc
         architecture = PSPNet
     model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
     if pretrained:
-        checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture_name}-{encoder}-{endocer_weights}.pt'
+        checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
         model.load_state_dict(torch.hub.load_state_dict_from_url(checkpoint, progress=False, map_location='cpu'))
     return model

### 2020-09-10 hubconf.py
add missing import

@@ -1,5 +1,6 @@
 dependencies = ['segmentation_models_pytorch']
 
+import torch
 from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
 
 

### 2020-09-16 ms.tex
fix Makefile {make test}

@@
 \begin{abstract}
-	Recently there has been an explosion in the use of Deep Learning (DL) methods for medical image segmentation.
-	However the field's reliability is hindered by the lack of a common base of reference for accuracy/performance evaluation and the fact that previous research uses different datasets for evaluation.
+	Deep Learning (DL) methods are extensively used for medical image segmentation.
+	However the field's reliability is hindered by the lack of a common base of reference for accuracy/performance evaluation and that previous research uses different datasets for evaluation.
 	In this paper, an extensive comparison of DL models for lung and COVID-19 lesion segmentation in Computerized Tomography (CT) scans is presented, which can also be used as a benchmark for testing medical image segmentation models.
@@
 	Three experimental setups are conducted for lung segmentation, lesion segmentation and lesion segmentation using the original lung masks.
-	A public COVID-19 dataset with $100$ CT scan images ($80$ for train, $20$ for validation) is used for training/validation and a different public dataset consisting of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes for testing.
+	A COVID-19 dataset with $100$ CT scan images is used for training/validation and a different dataset consisting of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes for testing.
 	Multiple findings are provided including the best architecture-encoder models for each experiment as well as mean Dice results for each experiment, architecture and encoder independently.
-	Finally, the upper bounds improvements when using lung masks as a preprocessing step or when using pretrained models are quantified.
 	The source code and $600$ pretrained models for the three experiments are provided, suitable for fine-tuning in experimental setups without GPU capabilities.

### 2020-11-11 ms.tex
init

@@
-\documentclass[journal]{IEEEtran}
+\documentclass{elsarticle}
 \usepackage[utf8]{inputenc}
@@
 \title{Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT scans}
-\author{Paschalis~Bizopoulos, Nicholas~Vretos and Petros~Daras, Senior Member, IEEE
-\thanks{P.
-Bizopoulos, N.
-Vretos and P.
-Daras are with the Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: \{pbizopoulos,vretos,daras\}@iti.gr}}
+\author[1]{Paschalis Bizopoulos}
+\author[1]{Nicholas Vretos}
+\author[1]{Petros Daras}
 
-\maketitle
+\address[1]{Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: \{pbizopoulos,vretos,daras\}@iti.gr}
 
@@
 
-\begin{IEEEkeywords}
+\begin{keyword}
 	COVID 19, deep learning, lung segmentation, lesion segmentation
-\end{IEEEkeywords}
+\end{keyword}
+
+\maketitle
 
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{4em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{results/lung-segmentation-hist}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{results/lung-segmentation-hist}}
 	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{results/lesion-segmentation-a-hist}}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1em}\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
 	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\best-masked-image}}
@@
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\best-masked-image}}
 	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\best-masked-image}}
@@
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\best-masked-image}}
 	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\best-masked-image}}
@@
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1em}\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
 	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\worst-masked-image}}
@@
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\worst-masked-image}}
 	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\worst-masked-image}}
@@
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.7em}\tiny Lesion segmentation B}\subfloat[Unet]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\worst-masked-image}}
-	\subfloat[Linknet]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\worst-masked-image}}
-	\subfloat[FPN]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\worst-masked-image}}
-	\subfloat[PSPNet]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\worst-masked-image}}
+	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\worst-masked-image}}
+	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\worst-masked-image}}
+	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\worst-masked-image}}
 	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
 \begin{figure}[!t]
-	\rotatebox[origin=l]{90}{\hspace{4em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-scatter-dice-vs-num-parameters}}
+	\centering
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-scatter-dice-vs-num-parameters}}
 	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{4em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
 	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{results/diff-scatter-dice-vs-num-parameters}}
@@
 	\setlength\tabcolsep{6.5pt}
-	\scalebox{0.64}{\input{results/metrics.tex}}
+	\scalebox{0.35}{\input{results/metrics.tex}}
 \end{table*}
@@
 \begin{figure}[!t]
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-train-loss}}
+	\centering
+	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-train-loss}}
 	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.2em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-train-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-train-loss}}
 	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.8em}\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-loss}}
 	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-loss}}
@@
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{1.3em}\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-diff-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-diff-loss}}
 	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-diff-loss}}
@@
 \begin{figure}[!t]
-	\rotatebox[origin=l]{90}{\hspace{3.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-boxplot-dice}}
+	\centering
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-boxplot-dice}}
 	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-boxplot-dice}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{3.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-boxplot-dice}}
 	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{results/initialization-boxplot-dice}}
@@
 \begin{figure}[!t]
-	\rotatebox[origin=l]{90}{\hspace{2.8em}\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-before-weights}}
+	\centering
+	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-before-weights}}
 	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-after-weights}}
@@
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{2.8em}\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-before-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-before-weights}}
 	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-after-weights}}
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{elsarticle-num}
 \bibliography{ms}

### 2020-11-11 utilities.py

@@ -1,0 +1,176 @@
+import numpy as np
+
+from matplotlib import gridspec
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from mpl_toolkits.mplot3d import Axes3D
+from scipy.stats import gaussian_kde
+from skimage.measure import marching_cubes
+
+plt.rcParams['image.interpolation'] = 'none'
+plt.rcParams['savefig.format'] = 'pdf'
+plt.rcParams['savefig.bbox'] = 'tight'
+
+
+def save_weights(model, experiment_name, architecture_name, encoder_weights, results_dir):
+    rows = 8
+    columns = 8
+    fig = plt.figure(figsize=(4, 4.6))
+    gs = gridspec.GridSpec(rows, columns, wspace=0.0, hspace=0.0, left=0)
+    for index_rows in range(rows):
+        for index_columns in range(columns):
+            weight = list(model.children())[0].conv1.weight[index_rows*rows+index_columns]
+            ax = plt.subplot(gs[index_rows, index_columns])
+            plt.imshow(weight[0].detach().cpu().numpy(), cmap='gray', vmin=-0.4, vmax=0.4)
+            ax.set_xticklabels([])
+            ax.set_yticklabels([])
+    plt.savefig(f'{results_dir}/{experiment_name}-{architecture_name}-{encoder_weights}-weights')
+    plt.close()
+
+def save_hist(hist_images, hist_masks, hist_range, experiment_name, results_dir):
+    t = np.linspace(hist_range[0], hist_range[1], hist_masks.shape[-1])
+    hist_images = hist_images.reshape(-1, hist_images.shape[-1]).sum(0)
+    hist_masks = hist_masks.reshape(-1, hist_masks.shape[-1]).sum(0)
+    hist_maxes = max([hist_images.max(), hist_masks.max()])
+    hist_images /= hist_maxes
+    hist_masks /= hist_maxes
+    fig, ax = plt.subplots()
+    plt.bar(t, hist_images, width=t[1]-t[0], align='center', label='Images')
+    plt.bar(t, hist_masks, width=t[1]-t[0], align='center', label='Masks')
+    plt.xlabel('Normalized values', fontsize=15)
+    plt.xlim(hist_range)
+    plt.ylim([10**(-7), 1])
+    plt.grid(True, which='both')
+    ax.set_yscale('log')
+    ax.legend()
[…]

### 2020-11-11 web-app/main.py

@@ -1,0 +1,73 @@
+import gradio
+import torch
+
+from matplotlib import pyplot as plt
+from torchvision.transforms import functional as tf
+
+from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
+
+
+experiment_list = ['Lung segmentation', 'Lesion segmentation A']
+experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
+architecture_list = [Unet, Linknet, FPN, PSPNet]
+architecture_name_list = [architecture.__name__ for architecture in architecture_list]
+encoder_list = ['vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6']
+encoder_weights_list = ['None', 'imagenet']
+
+def preprocess(image):
+    if image.shape[0] in [1, 3]:
+        image = image[0]
+    elif image.shape[-1] in [1, 3]:
+        image = image[..., -1]
+    image = tf.to_pil_image(image)
+    image = tf.resize(image, [512, 512])
+    image = tf.to_tensor(image)
+    image = tf.normalize(image, image.mean(), image.std())
+    return image.unsqueeze(0)
+
+
+def predict(image, experiment_name, architecture_name, encoder, encoder_weights):
+    if architecture_name == 'Unet':
+        architecture = Unet
+    if architecture_name == 'Linknet':
+        architecture = Linknet
+    if architecture_name == 'FPN':
+        architecture = FPN
+    if architecture_name == 'PSPNet':
+        architecture = PSPNet
+    model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
+    checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/latest/download/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
[…]

### 2020-11-12 web-app/main.py
simplify web-app

@@ -2,17 +2,9 @@ import gradio
 import torch
 
 from matplotlib import pyplot as plt
+from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
 from torchvision.transforms import functional as tf
 
-from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
-
-
-experiment_list = ['Lung segmentation', 'Lesion segmentation A']
-experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
-architecture_list = [Unet, Linknet, FPN, PSPNet]
-architecture_name_list = [architecture.__name__ for architecture in architecture_list]
-encoder_list = ['vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6']
-encoder_weights_list = ['None', 'imagenet']
 
 def preprocess(image):
     if image.shape[0] in [1, 3]:
@@ -24,7 +16,6 @@ def preprocess(image):
     image = tf.to_tensor(image)
     image = tf.normalize(image, image.mean(), image.std())
     return image.unsqueeze(0)
-
 
 def predict(image, experiment_name, architecture_name, encoder, encoder_weights):
     if architecture_name == 'Unet':
@@ -51,6 +42,12 @@ def predict(image, experiment_name, architecture_name, encoder, encoder_weights)
 
 
 if __name__ == '__main__':
+    experiment_list = ['Lung segmentation', 'Lesion segmentation A']
+    experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
+    architecture_list = [Unet, Linknet, FPN, PSPNet]
+    architecture_name_list = [architecture.__name__ for architecture in architecture_list]
[…]

### 2020-11-14 main.py
move variables in Makefile

@@ -23,11 +23,10 @@ if __name__ == '__main__':
     torch.manual_seed(0)
 
     parser = argparse.ArgumentParser()
+    parser.add_argument('cache_dir')
+    parser.add_argument('results_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
-
-    cache_dir = 'cache'
-    results_dir = 'results'
     # END OF DO NOT EDIT BLOCK
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
@@ -49,9 +48,9 @@ if __name__ == '__main__':
     experiment_list = ['Lung segmentation', 'Lesion segmentation A', 'Lesion segmentation B']
     experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
     encoder_weights_list = [None, 'imagenet']
-    train_dataset = MedicalSegmentation1(cache_dir, index_train_range, use_transforms=True)
+    train_dataset = MedicalSegmentation1(args.cache_dir, index_train_range, use_transforms=True)
     train_dataloader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
-    validation_dataset = MedicalSegmentation1(cache_dir, index_validation_range, use_transforms=False)
+    validation_dataset = MedicalSegmentation1(args.cache_dir, index_validation_range, use_transforms=False)
     validation_dataloader = DataLoader(validation_dataset, batch_size=batch_size)
     metric_list = ['Sens', 'Spec', 'Dice']
     metrics_array = np.zeros((len(experiment_list), len(architecture_list), len(encoder_list), len(encoder_weights_list), len(metric_list)))
@@ -72,7 +71,7 @@ if __name__ == '__main__':
                     num_parameters_array[index_architecture, index_encoder] = get_num_parameters(model)
                     optimizer = optim.Adam(model.parameters())
                     validation_loss_best = float('inf')
-                    model_path = f'{results_dir}/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
+                    model_path = f'{args.results_dir}/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
                     for index_epoch, epoch in enumerate(range(num_epochs)):
                         train_loss_sum = 0
                         model.train()
@@ -96,14 +95,14 @@ if __name__ == '__main__':
                                     predictions = model(images)
[…]

### 2020-11-29 main.py
simplify Makefile

@@ -17,8 +17,8 @@ from utilities import save_weights, save_hist, save_loss, save_scatter, save_arc
 if __name__ == '__main__':
     # DO NOT EDIT BLOCK - Required by the Makefile
     parser = argparse.ArgumentParser()
-    parser.add_argument('cache_dir')
     parser.add_argument('results_dir')
+    parser.add_argument('tmp_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
     # END OF DO NOT EDIT BLOCK
@@ -49,9 +49,9 @@ if __name__ == '__main__':
     experiment_list = ['Lung segmentation', 'Lesion segmentation A', 'Lesion segmentation B']
     experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
     encoder_weights_list = [None, 'imagenet']
-    train_dataset = MedicalSegmentation1(args.cache_dir, index_train_range, use_transforms=True)
+    train_dataset = MedicalSegmentation1(args.tmp_dir, index_train_range, use_transforms=True)
     train_dataloader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
-    validation_dataset = MedicalSegmentation1(args.cache_dir, index_validation_range, use_transforms=False)
+    validation_dataset = MedicalSegmentation1(args.tmp_dir, index_validation_range, use_transforms=False)
     validation_dataloader = DataLoader(validation_dataset, batch_size=batch_size)
     metric_list = ['Sens', 'Spec', 'Dice']
     metrics_array = np.zeros((len(experiment_list), len(architecture_list), len(encoder_list), len(encoder_weights_list), len(metric_list)))
@@ -145,7 +145,7 @@ if __name__ == '__main__':
                     model.eval()
                     num_slices_test = 0
                     for index_test_volume in index_test_volume_range:
-                        test_dataset = MedicalSegmentation2(args.cache_dir, index_test_volume, use_transforms=False)
+                        test_dataset = MedicalSegmentation2(args.tmp_dir, index_test_volume, use_transforms=False)
                         test_dataloader = DataLoader(test_dataset)
                         num_slices_test += len(test_dataloader)
                         with torch.no_grad():

### 2020-11-29 datasets.py
change cache_dir to tmp_dir

@@ -41,19 +41,19 @@ def preprocess(image, lung_mask, lesion_mask, use_transforms):
 
 
 class MedicalSegmentation1(Dataset):
-    def __init__(self, cache_dir, index_range, use_transforms):
+    def __init__(self, tmp_dir, index_range, use_transforms):
         urls = ['https://drive.google.com/uc?id=1SJoMelgRqb0EuqlTuq6dxBWf2j9Kno8S', 'https://drive.google.com/uc?id=1MEqpbpwXjrLrH42DqDygWeSkDq0bi92f', 'https://drive.google.com/uc?id=1zj4N_KV0LBko1VSQ7FPZ38eaEGNU0K6-']
         files = ['tr_im.nii.gz', 'tr_mask.nii.gz', 'tr_lungmasks_updated.nii.gz']
         for url, file in zip(urls, files):
-            if not os.path.isfile(f'{cache_dir}/{file}'):
-                gdown.download(url, f'{cache_dir}/{file}', quiet=False)
-        imgs_path = f'{cache_dir}/tr_im.nii.gz'
+            if not os.path.isfile(f'{tmp_dir}/{file}'):
+                gdown.download(url, f'{tmp_dir}/{file}', quiet=False)
+        imgs_path = f'{tmp_dir}/tr_im.nii.gz'
         images = nib.load(imgs_path)
         self.images = images.get_fdata()[..., index_range]
-        lesion_masks_path = f'{cache_dir}/tr_mask.nii.gz'
+        lesion_masks_path = f'{tmp_dir}/tr_mask.nii.gz'
         lesion_masks = nib.load(lesion_masks_path)
         self.lesion_masks = lesion_masks.get_fdata()[..., index_range]
-        lung_masks_path = f'{cache_dir}/tr_lungmasks_updated.nii.gz'
+        lung_masks_path = f'{tmp_dir}/tr_lungmasks_updated.nii.gz'
         lung_masks = nib.load(lung_masks_path)
         self.lung_masks = lung_masks.get_fdata()[..., index_range]
         self.use_transforms = use_transforms
@@ -67,27 +67,27 @@ class MedicalSegmentation1(Dataset):
 
 
 class MedicalSegmentation2(Dataset):
-    def __init__(self, cache_dir, index_volume, use_transforms):
+    def __init__(self, tmp_dir, index_volume, use_transforms):
[…]

### 2020-11-29 main.py

@@ -72,7 +72,7 @@ if __name__ == '__main__':
                     num_parameters_array[index_architecture, index_encoder] = get_num_parameters(model)
                     optimizer = optim.Adam(model.parameters())
                     validation_loss_best = float('inf')
-                    model_path = f'{args.results_dir}/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
+                    model_path = f'{args.tmp_dir}/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
                     for index_epoch, epoch in enumerate(range(num_epochs)):
                         train_loss_sum = 0
                         model.train()

### 2020-11-30 demos/main.py
fix demos

@@ -51,7 +51,7 @@ if __name__ == '__main__':
     gradio.reset_all()
     gradio.Interface(predict, 
             [
-                gradio.inputs.Image(shape=(512, 512, 1)),
+                gradio.inputs.Image(shape=(512, 512)),
                 gradio.inputs.Dropdown(experiment_name_list),
                 gradio.inputs.Dropdown(architecture_name_list),
                 gradio.inputs.Dropdown(encoder_list),

### 2020-11-30 ms.tex
fix README.md
simplify Makefile

@@
 \begin{document}
-\DTLloaddb{keys_values}{results/keys-values.csv}
+\DTLloaddb{keys_values}{tmp/keys-values.csv}
 
@@
 	\begin{tikzpicture}[]
-		\node[] (input) {\includegraphics[scale=0.3]{results/lesion-segmentation-a-image}};
+		\node[] (input) {\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-image}};
 		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
 		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
-		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{results/lesion-segmentation-a-prediction-train-masked-image}};
+		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-prediction-train-masked-image}};
 		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
-		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{results/lesion-segmentation-a-mask-train-masked-image}};
+		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-mask-train-masked-image}};
 		\node[] at (0, 1){$\bm{X}$};
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{results/lung-segmentation-hist}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{results/lesion-segmentation-a-hist}}
-	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{results/lesion-segmentation-b-hist}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{tmp/lung-segmentation-hist}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-a-hist}}
+	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-b-hist}}
 	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\worst-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\worst-masked-image}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\worst-masked-image}}
-	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\worst-masked-image}}
-	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\worst-masked-image}}
-	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\worst-masked-image}}
+	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\worst-masked-image}}
+	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\worst-masked-image}}
+	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\worst-masked-image}}
 	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{results/diff-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{tmp/diff-scatter-dice-vs-num-parameters}}
 	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
@@
 	\setlength\tabcolsep{6.5pt}
-	\scalebox{0.35}{\input{results/metrics.tex}}
+	\scalebox{0.35}{\input{tmp/metrics.tex}}
 \end{table*}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-loss}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-diff-loss}}
-	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-diff-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-diff-loss}}
+	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-diff-loss}}
 	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-boxplot-dice}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-boxplot-dice}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-boxplot-dice}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-boxplot-dice}}
-	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{results/initialization-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-boxplot-dice}}
+	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{tmp/initialization-boxplot-dice}}
 	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-PSPNet-None-volume}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-PSPNet-None-volume}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-mask--volume}}
-	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-Unet-None-volume}}
-	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-Linknet-None-volume}}
-	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-FPN-None-volume}}
-	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-mask--volume}}
+	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Unet-None-volume}}
+	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Linknet-None-volume}}
+	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-FPN-None-volume}}
+	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-PSPNet-None-volume}}
 	\caption{Reconstructed volumes from predicted masks.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-before-weights}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-before-weights}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-after-weights}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-before-weights}}
-	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-before-weights}}
+	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-after-weights}}
 	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{ms}
+\bibliography{ms.bib}
 

### 2020-11-30 datasets.py

@@ -41,19 +41,19 @@ def preprocess(image, lung_mask, lesion_mask, use_transforms):
 
 
 class MedicalSegmentation1(Dataset):
-    def __init__(self, tmp_dir, index_range, use_transforms):
+    def __init__(self, index_range, use_transforms):
         urls = ['https://drive.google.com/uc?id=1SJoMelgRqb0EuqlTuq6dxBWf2j9Kno8S', 'https://drive.google.com/uc?id=1MEqpbpwXjrLrH42DqDygWeSkDq0bi92f', 'https://drive.google.com/uc?id=1zj4N_KV0LBko1VSQ7FPZ38eaEGNU0K6-']
         files = ['tr_im.nii.gz', 'tr_mask.nii.gz', 'tr_lungmasks_updated.nii.gz']
         for url, file in zip(urls, files):
-            if not os.path.isfile(f'{tmp_dir}/{file}'):
-                gdown.download(url, f'{tmp_dir}/{file}', quiet=False)
-        imgs_path = f'{tmp_dir}/tr_im.nii.gz'
+            if not os.path.isfile(f'tmp/{file}'):
+                gdown.download(url, f'tmp/{file}', quiet=False)
+        imgs_path = f'tmp/tr_im.nii.gz'
         images = nib.load(imgs_path)
         self.images = images.get_fdata()[..., index_range]
-        lesion_masks_path = f'{tmp_dir}/tr_mask.nii.gz'
+        lesion_masks_path = f'tmp/tr_mask.nii.gz'
         lesion_masks = nib.load(lesion_masks_path)
         self.lesion_masks = lesion_masks.get_fdata()[..., index_range]
-        lung_masks_path = f'{tmp_dir}/tr_lungmasks_updated.nii.gz'
+        lung_masks_path = f'tmp/tr_lungmasks_updated.nii.gz'
         lung_masks = nib.load(lung_masks_path)
         self.lung_masks = lung_masks.get_fdata()[..., index_range]
         self.use_transforms = use_transforms
@@ -67,27 +67,27 @@ class MedicalSegmentation1(Dataset):
 
 
 class MedicalSegmentation2(Dataset):
-    def __init__(self, tmp_dir, index_volume, use_transforms):
+    def __init__(self, index_volume, use_transforms):
[…]

### 2020-11-30 main.py

@@ -17,8 +17,6 @@ from utilities import save_weights, save_hist, save_loss, save_scatter, save_arc
 if __name__ == '__main__':
     # DO NOT EDIT BLOCK - Required by the Makefile
     parser = argparse.ArgumentParser()
-    parser.add_argument('results_dir')
-    parser.add_argument('tmp_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
     # END OF DO NOT EDIT BLOCK
@@ -49,9 +47,9 @@ if __name__ == '__main__':
     experiment_list = ['Lung segmentation', 'Lesion segmentation A', 'Lesion segmentation B']
     experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
     encoder_weights_list = [None, 'imagenet']
-    train_dataset = MedicalSegmentation1(args.tmp_dir, index_train_range, use_transforms=True)
+    train_dataset = MedicalSegmentation1(index_train_range, use_transforms=True)
     train_dataloader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
-    validation_dataset = MedicalSegmentation1(args.tmp_dir, index_validation_range, use_transforms=False)
+    validation_dataset = MedicalSegmentation1(index_validation_range, use_transforms=False)
     validation_dataloader = DataLoader(validation_dataset, batch_size=batch_size)
     metric_list = ['Sens', 'Spec', 'Dice']
     metrics_array = np.zeros((len(experiment_list), len(architecture_list), len(encoder_list), len(encoder_weights_list), len(metric_list)))
@@ -72,7 +70,7 @@ if __name__ == '__main__':
                     num_parameters_array[index_architecture, index_encoder] = get_num_parameters(model)
                     optimizer = optim.Adam(model.parameters())
                     validation_loss_best = float('inf')
-                    model_path = f'{args.tmp_dir}/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
+                    model_path = f'tmp/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
                     for index_epoch, epoch in enumerate(range(num_epochs)):
                         train_loss_sum = 0
                         model.train()
@@ -96,14 +94,14 @@ if __name__ == '__main__':
                                     predictions = model(images)
                                 train_time_array[index_experiment_name, index_architecture, index_encoder, index_encoder_weights] += sum([item.cpu_time for item in prof.function_events])
[…]

### 2020-11-30 utilities.py

@@ -12,7 +12,7 @@ plt.rcParams['savefig.format'] = 'pdf'
 plt.rcParams['savefig.bbox'] = 'tight'
 
 
-def save_weights(model, experiment_name, architecture_name, encoder_weights, results_dir):
+def save_weights(model, experiment_name, architecture_name, encoder_weights):
     rows = 8
     columns = 8
     fig = plt.figure(figsize=(4, 4.6))
@@ -24,10 +24,10 @@ def save_weights(model, experiment_name, architecture_name, encoder_weights, res
             plt.imshow(weight[0].detach().cpu().numpy(), cmap='gray', vmin=-0.4, vmax=0.4)
             ax.set_xticklabels([])
             ax.set_yticklabels([])
-    plt.savefig(f'{results_dir}/{experiment_name}-{architecture_name}-{encoder_weights}-weights')
+    plt.savefig(f'tmp/{experiment_name}-{architecture_name}-{encoder_weights}-weights')
     plt.close()
 
-def save_hist(hist_images, hist_masks, hist_range, experiment_name, results_dir):
+def save_hist(hist_images, hist_masks, hist_range, experiment_name):
     t = np.linspace(hist_range[0], hist_range[1], hist_masks.shape[-1])
     hist_images = hist_images.reshape(-1, hist_images.shape[-1]).sum(0)
     hist_masks = hist_masks.reshape(-1, hist_masks.shape[-1]).sum(0)
@@ -43,10 +43,10 @@ def save_hist(hist_images, hist_masks, hist_range, experiment_name, results_dir)
     plt.grid(True, which='both')
     ax.set_yscale('log')
     ax.legend()
-    plt.savefig(f'{results_dir}/{experiment_name}-hist')
+    plt.savefig(f'tmp/{experiment_name}-hist')
     plt.close()
 
-def save_loss(loss, train_or_validation, experiment_name, architecture_name_list, ylim, results_dir):
+def save_loss(loss, train_or_validation, experiment_name, architecture_name_list, ylim):
     loss = np.nan_to_num(loss)
     color_list = plt.rcParams['axes.prop_cycle'].by_key()['color']
     p1 = [None]*len(architecture_name_list)
@@ -69,30 +69,30 @@ def save_loss(loss, train_or_validation, experiment_name, architecture_name_list
     ax.tick_params(axis='both', which='major', labelsize='large')
     ax.tick_params(axis='both', which='minor', labelsize='large')
[…]

### 2021-02-03 ms.tex
fix email

@@
 
-\address[1]{Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: \{pbizopoulos,vretos,daras\}@iti.gr}
+\address[1]{Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com,\{vretos,daras\}@iti.gr}
 

### 2021-08-28 ms.tex
init

@@
 \begin{document}
-\DTLloaddb{keys_values}{tmp/keys-values.csv}
+\DTLloaddb{keys-values}{tmp/keys-values.csv}
 
@@
 	Three experimental setups are conducted for lung segmentation, lesion segmentation and lesion segmentation using the original lung masks.
-	A COVID-19 dataset with $100$ CT scan images is used for training/validation and a different dataset consisting of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes for testing.
+	A COVID-19 dataset with $100$ CT scan images is used for training/validation and a different dataset consisting of $\DTLfetch{keys-values}{key}{num-slices-test}{value}$ images from $9$ CT scan volumes for testing.
 	Multiple findings are provided including the best architecture-encoder models for each experiment as well as mean Dice results for each experiment, architecture and encoder independently.
@@
 
-\section{Introduction}
-\label{sec:introduction}
+\section{Introduction}\label{sec:introduction}
 Coronavirus Disease 2019 (COVID-19) has emerged in December of 2019 and was declared as a pandemic in March of 2020~\cite{world2020coronavirus}.
@@
 
-\section{Methods}
+\section{Methods}\label{sec:methods}
 In this Section the problem of segmentation is formalized and the architectures and encoders that are used in this study are presented.
 
-\label{sec:methods}
 \subsection{Formalization}
@@
 	Then $\hat{\bm{Y}}$ and $\bm{Y}$ are used to calculate the loss, which is then used to backpropagate the error to the weights.
-	This procedure is repeated for a number of times using more training examples till $\mathcal{L}$ converges.}
-	\label{fig:highleveloverview}
+	This procedure is repeated for a number of times using more training examples till $\mathcal{L}$ converges.}\label{fig:highleveloverview}
 \end{figure}
 
-\subsection{Architectures}
-\label{sec:architectures}
+\subsection{Architectures}\label{sec:architectures}
 Four architectures are used as the basis of the models to be tested:
@@
 
-\subsection{Encoders}
-\label{sec:encoders}
+\subsection{Encoders}\label{sec:encoders}
 The following encoders are used along with their variations denoted in the parenthesis:
@@
 
-\section{Datasets}
-\label{sec:datasets}
+\section{Datasets}\label{sec:datasets}
 Two public COVID-19 CT scan datasets with lung and lesion masks were used.
@@
 The original dataset, without the annotations, was selected from the Italian Society of Medical and Interventional Radiology\footnote{\url{https://www.sirm.org/category/senza-categoria/covid-19/}}.
-The second dataset\footnote{\url{https://radiopaedia.org/articles/covid-19-3}} consists of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes (a set of CT scan images acquired from the same patient at the same moment) with corresponding target masks.
-373 out of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ were annotated as positive and segmented by a radiologist by the same group as the first dataset.
+The second dataset\footnote{\url{https://radiopaedia.org/articles/covid-19-3}} consists of $\DTLfetch{keys-values}{key}{num-slices-test}{value}$ images from $9$ CT\@ scan volumes (a set of CT scan images acquired from the same patient at the same moment) with corresponding target masks.
+373 out of $\DTLfetch{keys-values}{key}{num-slices-test}{value}$ were annotated as positive and segmented by a radiologist by the same group as the first dataset.
 Raw data from both datasets contain samples in Hounsfield units~\cite{schneider1996calibration}.
@@
 In Fig.~\ref{fig:hist} the histograms of the pixel intensities of all the CT scan images and the target masks in the test dataset after normalization, for each of the three experiments, are depicted.
-The considerable overlap between the histograms makes the use of thresholding models in this kind of problem unsuitable, thus justifying the use of learning models such as DL.
+The considerable overlap between the histograms makes the use of thresholding models in this kind of problem unsuitable, thus justifying the use of learning models such as DL\@.
 
@@
 	The vertical axis depicts the normalized frequencies of each pixel intensity in the logarithmic scale.
-	The outlier bar at zero is because most of the pixels in the target masks are near zero.}
-	\label{fig:hist}
+	The outlier bar at zero is because most of the pixels in the target masks are near zero.}\label{fig:hist}
 \end{figure*}
 
-\section{Experimental setup}
-\label{sec:experimentalsetup}
+\section{Experimental setup}\label{sec:experimentalsetup}
 In this Section the experimental setup is presented.
@@
 
-Each model is constructed using a unique combination of the four architectures described in subsection~\ref{sec:architectures} and the $25$ encoders referenced in subsection~\ref{sec:encoders}.
+Each model is constructed using a unique combination of the four architectures described in Subsection~\ref{sec:architectures} and the $25$ encoders referenced in Subsection~\ref{sec:encoders}.
 The selection of architectures and encoders was based on the restriction of the GPU memory of our graphics card, combined with the value of batch size.
@@
 	\centering
-	\caption{Architecture hyperparameters}
-	\label{table:architecturehyperparameters}
-	\begin{tabular}{l|c|c|c}
+	\caption{Architecture hyperparameters}\label{table:architecturehyperparameters}
+	\begin{tabular}{lccc}
 		\toprule
@@
 
-We train a total of $600$ different models for the three experiments each one for $\DTLfetch{keys_values}{key}{num_epochs}{value}$ epochs with a batch size of $\DTLfetch{keys_values}{key}{batch_size}{value}$, which was the maximum possible considering the GPU memory restriction.
+We train a total of $600$ different models for the three experiments each one for $\DTLfetch{keys-values}{key}{num-epochs}{value}$ epochs with a batch size of $\DTLfetch{keys-values}{key}{batch-size}{value}$, which was the maximum possible considering the GPU memory restriction.
 We use the optimizer~\cite{kingma2014adam} with the default values of learning rate $0.001$, $\beta_1=0.9$, $\beta_2=0.999$, $\epsilon=10^{-8}$, without weight decay.
@@
 \begin{algorithm}[H]
-	\caption{Experimental setup}
-	\label{alg:experimentalsetup}
+	\caption{Experimental setup}\label{alg:experimentalsetup}
 	\begin{algorithmic}[1]
@@
 		\renewcommand{\algorithmicensure}{\textbf{Output:}}
-		\REQUIRE $epochs$
-		\ENSURE $metrics$
+		\REQUIRE{$epochs$}
+		\ENSURE{$metrics$}
 		\\ \textit{Hyperparameters:  $\lambda$, $batches$}
@@
 		\FOR {$b$ = 1 to $batches$}
-		\STATE $\bm{Y}_{train}, \bm{X}_{train} \sim \mathcal{D}_{train}$
-		\STATE $\bm{Y}_{train}, \bm{X}_{train} \leftarrow Augm(\bm{Y}_{train}, \bm{X}_{train})$
-		\STATE $\hat{\bm{Y}}_{train} \leftarrow m_{ex, ar, en, ew}(\bm{X}_{train})$
-		\STATE $\mathcal{L}_{train} \leftarrow DiceLoss(\hat{\bm{Y}}_{train}, \bm{Y}_{train})$
-		\STATE $\nabla\mathcal{L}_{train} = \left( \frac{\partial\mathcal{L}}{\partial\bm{w}^{(1)}},\ldots\frac{\partial\mathcal{L}}{\partial\bm{w}^{(q)}}\right)$
-		\STATE $\Delta\bm{w}^{(i)} \leftarrow -\lambda\frac{\partial\mathcal{L}}{\partial\bm{w}^{(i)}}$
-		\ENDFOR
+		\STATE{$\bm{Y}_{train}, \bm{X}_{train} \sim \mathcal{D}_{train}$}
+		\STATE{$\bm{Y}_{train}, \bm{X}_{train} \leftarrow Augm(\bm{Y}_{train}, \bm{X}_{train})$}
+		\STATE{$\hat{\bm{Y}}_{train} \leftarrow m_{ex, ar, en, ew}(\bm{X}_{train})$}
+		\STATE{$\mathcal{L}_{train} \leftarrow DiceLoss(\hat{\bm{Y}}_{train}, \bm{Y}_{train})$}
+		\STATE{$\nabla\mathcal{L}_{train} = \left( \frac{\partial\mathcal{L}}{\partial\bm{w}^{(1)}},\ldots\frac{\partial\mathcal{L}}{\partial\bm{w}^{(q)}}\right)$}
+		\STATE{$\Delta\bm{w}^{(i)} \leftarrow -\lambda\frac{\partial\mathcal{L}}{\partial\bm{w}^{(i)}}$}
+		\ENDFOR{}
 		\FOR {$b$ = 1 to $batches$}
-		\STATE $\bm{Y}_{val}, \bm{X}_{val} \sim \mathcal{D}_{val}$
-		\STATE $\hat{\bm{Y}}_{val} \leftarrow m_{ex, ar, en, ew}(\bm{X}_{val})$
-		\STATE $\mathcal{L}_{val} \leftarrow DiceLoss(\hat{\bm{Y}}_{val}, \bm{Y}_{val})$
-		\ENDFOR
+		\STATE{$\bm{Y}_{val}, \bm{X}_{val} \sim \mathcal{D}_{val}$}
+		\STATE{$\hat{\bm{Y}}_{val} \leftarrow m_{ex, ar, en, ew}(\bm{X}_{val})$}
+		\STATE{$\mathcal{L}_{val} \leftarrow DiceLoss(\hat{\bm{Y}}_{val}, \bm{Y}_{val})$}
+		\ENDFOR{}
 		\IF{$\mathcal{L}_{val} < \mathcal{L}_{val}^{best}$}
-		\STATE $m_{ex, ar, en, ew}^{best} \leftarrow m_{ex, ar, en, ew}$
-		\ENDIF
-		\ENDFOR
-		\STATE $\hat{\bm{Y}}_{test} \leftarrow m_{ex, ar, en, ew}^{best}(\bm{X}_{test})$
-		\STATE $metrics_{ex, ar, en, ew} = metrics(\hat{\bm{Y}}_{test}, \bm{Y}_{test})$
-		\ENDFOR
-		\ENDFOR
-		\ENDFOR
-		\ENDFOR
-		\RETURN $metrics$
+		\STATE{$m_{ex, ar, en, ew}^{best} \leftarrow m_{ex, ar, en, ew}$}
+		\ENDIF{}
+		\ENDFOR{}
+		\STATE{$\hat{\bm{Y}}_{test} \leftarrow m_{ex, ar, en, ew}^{best}(\bm{X}_{test})$}
+		\STATE{$metrics_{ex, ar, en, ew} = metrics(\hat{\bm{Y}}_{test}, \bm{Y}_{test})$}
+		\ENDFOR{}
+		\ENDFOR{}
+		\ENDFOR{}
+		\ENDFOR{}
+		\RETURN{$metrics$}
 	\end{algorithmic}
@@
 
-\section{Results}
-\label{sec:results}
+\section{Results}\label{sec:results}
 In this Section the results of the three experimental setups are demonstrated, along with several comparisons between experiments, architectures, encoders and weight initialization schemes.
@@
 The best combination of architecture-encoder for each combination of encoder weight initialization, experimental setup and metric are showin in bold.
-The mean Dice results for each experiment are $\DTLfetch{keys_values}{key}{lung-segmentation-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-imagenet-std}{value}\%$, for `lesion segmentation A' and $\DTLfetch{keys_values}{key}{lesion-segmentation-b-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-imagenet-std}{value}\%$, for `lesion segmentation B'.
-The best performing models w.r.t.\ Dice for each experiment were the \DTLfetch{keys_values}{key}{lung-segmentation-architecture-imagenet-index-max}{value}-\DTLfetch{keys_values}{key}{lung-segmentation-encoder-imagenet-index-max}{value} ($\DTLfetch{keys_values}{key}{lung-segmentation-imagenet-max}{value}\%$) for lung segmentation, \DTLfetch{keys_values}{key}{lesion-segmentation-a-architecture-imagenet-index-max}{value}-\DTLfetch{keys_values}{key}{lesion-segmentation-a-encoder-imagenet-index-max}{value} ($\DTLfetch{keys_values}{key}{lesion-segmentation-a-imagenet-max}{value}\%$) for lesion segmentation A and \DTLfetch{keys_values}{key}{lesion-segmentation-b-architecture-imagenet-index-max}{value}-\DTLfetch{keys_values}{key}{lesion-segmentation-b-encoder-imagenet-index-max}{value} ($\DTLfetch{keys_values}{key}{lesion-segmentation-b-imagenet-max}{value}\%$) for lesion segmentation B.
-In Fig.~\ref{fig:predictedmasks} the predicted masks for $24$ out of the $600$ models are depicted, demonstrating the difference in segmentation quality between the best (\DTLfetch{keys_values}{key}{encoder-best}{value}) and the worst (\DTLfetch{keys_values}{key}{encoder-worst}{value}) performing encoder of the models for each architecture, with randomly initialized weights.
+The mean Dice results for each experiment are $\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-std}{value}\%$, for `lesion segmentation A' and $\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-std}{value}\%$, for `lesion segmentation B'.
+The best performing models w.r.t.\ Dice for each experiment were the \DTLfetch{keys-values}{key}{lung-segmentation-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lung-segmentation-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-max}{value}\%$) for lung segmentation, \DTLfetch{keys-values}{key}{lesion-segmentation-a-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lesion-segmentation-a-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-max}{value}\%$) for lesion segmentation A and \DTLfetch{keys-values}{key}{lesion-segmentation-b-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lesion-segmentation-b-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-max}{value}\%$) for lesion segmentation B.
+In Fig.~\ref{fig:predictedmasks} the predicted masks for $24$ out of the $600$ models are depicted, demonstrating the difference in segmentation quality between the best (\DTLfetch{keys-values}{key}{encoder-best}{value}) and the worst (\DTLfetch{keys-values}{key}{encoder-worst}{value}) performing encoder of the models for each architecture, with randomly initialized weights.
 In Fig.~\ref{fig:dicevsnumparameters} the Dice vs.\ the number of parameters is plotted, demonstrating that there is positive correlation, suggesting that segmentation generally improves when using higher number of parameters.
@@
 
-\DTLfetchsave{\best}{keys_values}{key}{encoder-best}{value}
-\DTLfetchsave{\worst}{keys_values}{key}{encoder-worst}{value}
+\DTLfetchsave{\best}{keys-values}{key}{encoder-best}{value}
+\DTLfetchsave{\worst}{keys-values}{key}{encoder-worst}{value}
 
@@
 	Rows correspond to each of the four architectures.
-	Green and red depict correctly and falsely classified pixels respectively.}
-	\label{fig:predictedmasks}
+	Green and red depict correctly and falsely classified pixels respectively.}\label{fig:predictedmasks}
 \end{figure}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-scatter-dice-vs-num-parameters}}
 	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
 	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{tmp/diff-scatter-dice-vs-num-parameters}}
@@
 	The green regions depict the kernel density estimate for all points using Gaussian kernels.
-	The method used to calculate the estimator bandwidth was Scott and the points are assumed to be equally weighted.}
-	\label{fig:dicevsnumparameters}
+	The method used to calculate the estimator bandwidth was Scott and the points are assumed to be equally weighted.}\label{fig:dicevsnumparameters}
 \end{figure}
@@
 	\centering
-	\caption{Metrics}
-	\label{table:metrics}
+	\caption{Metrics}\label{table:metrics}
 	\setlength\tabcolsep{6.5pt}
@@
 	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
-	Rows correspond to experimental setups and the difference between lesion segmentation B and A and columns correspond to train and validation losses.}
-	\label{fig:loss}
+	Rows correspond to experimental setups and the difference between lesion segmentation B and A and columns correspond to train and validation losses.}\label{fig:loss}
 \end{figure}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-boxplot-dice}}
 	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-boxplot-dice}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-boxplot-dice}}
 	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{tmp/initialization-boxplot-dice}}
-	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}
-	\label{fig:box}
+	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}\label{fig:box}
 \end{figure}
 
-The mean Dice results for Unet are $\DTLfetch{keys_values}{key}{lung-segmentation-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-Unet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-Unet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-Unet-imagenet-std}{value}\%$ for `lesion segmentation B'.
-The mean Dice results for Linknet are $\DTLfetch{keys_values}{key}{lung-segmentation-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-Linknet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-Linknet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-Linknet-imagenet-std}{value}\%$ for `lesion segmentation B'.
-The mean Dice results for FPN are $\DTLfetch{keys_values}{key}{lung-segmentation-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-FPN-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-FPN-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-FPN-imagenet-std}{value}\%$ for `lesion segmentation B'.
-The mean Dice results for PSPNet are $\DTLfetch{keys_values}{key}{lung-segmentation-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lung-segmentation-PSPNet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys_values}{key}{lesion-segmentation-a-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-a-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys_values}{key}{lesion-segmentation-b-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{lesion-segmentation-b-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for Unet are $\DTLfetch{keys-values}{key}{lung-segmentation-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-Unet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-Unet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-Unet-imagenet-std}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for Linknet are $\DTLfetch{keys-values}{key}{lung-segmentation-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-Linknet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-Linknet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-Linknet-imagenet-std}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for FPN are $\DTLfetch{keys-values}{key}{lung-segmentation-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-FPN-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-FPN-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-FPN-imagenet-std}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for PSPNet are $\DTLfetch{keys-values}{key}{lung-segmentation-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-PSPNet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation B'.
 
@@
 	\caption{Reconstructed volumes from predicted masks.
-	Reconstruction was done by stacking the predicted masks on the z-axis and then applying the marching cubes algorithm.}
-	\label{fig:volumes}
+	Reconstruction was done by stacking the predicted masks on the z-axis and then applying the marching cubes algorithm.}\label{fig:volumes}
 \end{figure*}
@@
 In Fig.~\ref{fig:weights} the weights are depicted, in which we observe that with random initialization the weights depict high and low frequency textures after training.
-The Dice for using random initialization is $\DTLfetch{keys_values}{key}{None-mean}{value}\%\pm\DTLfetch{keys_values}{key}{None-std}{value}\%$ and for ImageNet initialization is $\DTLfetch{keys_values}{key}{imagenet-mean}{value}\%\pm\DTLfetch{keys_values}{key}{imagenet-std}{value}\%$.
+The Dice for using random initialization is $\DTLfetch{keys-values}{key}{None-mean}{value}\%\pm\DTLfetch{keys-values}{key}{None-std}{value}\%$ and for ImageNet initialization is $\DTLfetch{keys-values}{key}{imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{imagenet-std}{value}\%$.
 
@@
 	The two left and two right grids correspond to random and ImageNet pretrained initialization, respectively.
-	The data range of the colormap of the images has been adjusted in the range $[-0.4, 0.4]$.}
-	\label{fig:weights}
+	The data range of the colormap of the images has been adjusted in the range $[-0.4, 0.4]$.}\label{fig:weights}
 \end{figure}
 
-\section{Discussion}
-\label{sec:discussion}
+\section{Discussion}\label{sec:discussion}
 A motivation for this study is that the large amount of new models that are proposed, rarely conduct ablation studies and do not compare with simple baselines.
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
+\section{Conclusions}\label{sec:conclusions}
 The need for fast, accurate and automatic diagnosis of COVID-19 requires highly reliable and publicly available models.
-We demonstrate specific properties that increase model segmentation and help experts in improved diagnosis by publicly providing pretrained models ready to be used for fine-tuning in experimental setups without GPU.
+We demonstrate specific properties that increase model segmentation and help experts in improved diagnosis by publicly providing pretrained models ready to be used for fine-tuning in experimental setups without GPU\@.
 

### 2021-08-28 hubconf.py

@@ -1,0 +1,28 @@
+dependencies = ['segmentation_models_pytorch']
+
+import torch
+from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
+
+
+def segmentation_model(pretrained=True, experiment_name='lung-segmentation', architecture_name='Unet', encoder='resnet18', encoder_weights='imagenet'):
+    """
+    segmentation model
+    pretrained (bool): load pretrained weights into the model
+    experiment_name ('lung-segmentation', 'lesion-segmentation-a'): Experiment name
+    architecture_name ('Unet', 'Linknet', 'FPN', 'PSPNet'): Architecture name
+    encoder ('vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6'): Encoder
+    encoder_weights (None, 'imagenet'): Encoder weights
+    """
+    if architecture_name == 'Unet':
+        architecture = Unet
+    if architecture_name == 'Linknet':
+        architecture = Linknet
+    if architecture_name == 'FPN':
+        architecture = FPN
+    if architecture_name == 'PSPNet':
+        architecture = PSPNet
+    model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
+    if pretrained:
+        checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/download/v1/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
+        model.load_state_dict(torch.hub.load_state_dict_from_url(checkpoint, progress=False, map_location='cpu'))
+    return model

### 2021-08-28 main.py

@@ -1,0 +1,616 @@
+import argparse
+import glob
+import itertools
+import os
+from zipfile import ZipFile
+
+import gdown
+import nibabel as nib
+import numpy as np
+import pandas as pd
+import requests
+import torch
+from matplotlib import gridspec
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from mpl_toolkits.mplot3d import Axes3D
+from scipy.stats import gaussian_kde
+from segmentation_models_pytorch import FPN, Linknet, PSPNet, Unet
+from segmentation_models_pytorch.utils.losses import DiceLoss
+from skimage.measure import marching_cubes
+from torch import optim
+from torch.utils.data import DataLoader, Dataset
+from torchvision.transforms import functional as tf
+
+plt.rcParams['image.interpolation'] = 'none'
+plt.rcParams['savefig.format'] = 'pdf'
+plt.rcParams['savefig.bbox'] = 'tight'
+
+eps = 1e-6
+
+
+def metrics(prediction, mask):
+    prediction = prediction > 0.5
+    true_positive = (mask * prediction).sum().float()
+    true_negative = (~mask * ~prediction).sum().float()
+    false_positive = (mask * ~prediction).sum().float()
+    false_negative = (~mask * prediction).sum().float()
+    is_mask_and_prediction_empty = (true_positive + false_positive) == 0
+    if is_mask_and_prediction_empty:
+        specificity = 1
+        sensitivity = 1
+        dice = 1
+    else:
+        specificity = (true_negative / (true_negative + false_positive + eps)).item()
+        sensitivity = (true_positive / (true_positive + false_negative + eps)).item()
+        dice = (2 * true_positive / (2 * true_positive + false_positive + false_negative + eps)).item()
+    return sensitivity, specificity, dice
+
+
+def save_weights(model, experiment_name, architecture_name, encoder_weights):
+    rows = 8
+    columns = 8
+    plt.figure(figsize=(4, 4.6))
+    gs = gridspec.GridSpec(rows, columns, wspace=0.0, hspace=0.0, left=0)
+    for index_rows in range(rows):
+        for index_columns in range(columns):
[…]

### 2021-08-31 ms.tex
init

@@
 \usepackage{amssymb}
+\usepackage{adjustbox}
 \usepackage{tabularx}
@@
 		\toprule
-		\textbf{Architecture} & \textbf{\makecell{Encoder\\ depth}}          & \textbf{Batch Norm}                & \textbf{Various}                                                                                             \\ \hline
-		Unet    & 5 & Yes (decoder) & \makecell{decoder channel sizes =\\ (256, 128, 64, 32, 16)}                                 \\ \hline
-		Linknet & 5 & Yes (decoder) & -                                                                              \\ \hline
-		FPN     & 5 & No            & \makecell{pyramid channels=256,\\ segment channels=128,\\ merge policy=add,\\ dropout=0.2} \\ \hline
-		PSPNet  & 3 & Yes (encoder) & \makecell{output channels=512,\\ dropout=0.2}                                              \\ \hline
+		\textbf{Architecture} & \textbf{\makecell{Encoder\\ depth}}          & \textbf{Batch Norm}                & \textbf{Various}                                                                                             \\
+		Unet    & 5 & Yes (decoder) & \makecell{decoder channel sizes =\\ (256, 128, 64, 32, 16)}                                 \\
+		\midrule
+		Linknet & 5 & Yes (decoder) & -                                                                              \\
+		\midrule
+		FPN     & 5 & No            & \makecell{pyramid channels=256,\\ segment channels=128,\\ merge policy=add,\\ dropout=0.2} \\
+		\midrule
+		PSPNet  & 3 & Yes (encoder) & \makecell{output channels=512,\\ dropout=0.2}                                              \\
+		\bottomrule
 	\end{tabular}
@@
 		\\ \textit{Hyperparameters:  $\lambda$, $batches$}
-		\FOR {$ex$ = 1 to $n_{experiments}$}
-		\FOR {$ar$ = 1 to $n_{architectures}$}
-		\FOR {$en$ = 1 to $n_{encoders}$}
-		\FOR {$ew$ = 1 to $n_{encoder\ weights}$}
-		\FOR {$ep$ = 1 to $epochs$}
-		\FOR {$b$ = 1 to $batches$}
+		\FOR{$ex$ = 1 to $n_{experiments}$}
+		\FOR{$ar$ = 1 to $n_{architectures}$}
+		\FOR{$en$ = 1 to $n_{encoders}$}
+		\FOR{$ew$ = 1 to $n_{encoder\ weights}$}
+		\FOR{$ep$ = 1 to $epochs$}
+		\FOR{$b$ = 1 to $batches$}
 		\STATE{$\bm{Y}_{train}, \bm{X}_{train} \sim \mathcal{D}_{train}$}
@@
 		\ENDFOR{}
-		\FOR {$b$ = 1 to $batches$}
+		\FOR{$b$ = 1 to $batches$}
 		\STATE{$\bm{Y}_{val}, \bm{X}_{val} \sim \mathcal{D}_{val}$}
@@
 	\caption{Metrics}\label{table:metrics}
-	\setlength\tabcolsep{6.5pt}
-	\scalebox{0.35}{\input{tmp/metrics.tex}}
+	\begin{adjustbox}{width=\textwidth}
+		\input{tmp/metrics.tex}
+	\end{adjustbox}
 \end{table*}

### 2021-08-31 gradio/main.py

@@ -1,0 +1,70 @@
+import gradio
+import torch
+
+from matplotlib import pyplot as plt
+from segmentation_models_pytorch import Unet, Linknet, FPN, PSPNet
+from torchvision.transforms import functional as tf
+
+
+def preprocess(image):
+    if image.shape[0] in [1, 3]:
+        image = image[0]
+    elif image.shape[-1] in [1, 3]:
+        image = image[..., -1]
+    image = tf.to_pil_image(image)
+    image = tf.resize(image, [512, 512])
+    image = tf.to_tensor(image)
+    image = tf.normalize(image, image.mean(), image.std())
+    return image.unsqueeze(0)
+
+def predict(image, experiment_name, architecture_name, encoder, encoder_weights):
+    if architecture_name == 'Unet':
+        architecture = Unet
+    if architecture_name == 'Linknet':
+        architecture = Linknet
+    if architecture_name == 'FPN':
+        architecture = FPN
+    if architecture_name == 'PSPNet':
+        architecture = PSPNet
+    model = architecture(encoder, encoder_weights=encoder_weights, activation='sigmoid', in_channels=1).to('cpu')
+    checkpoint = f'https://github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/releases/latest/download/{experiment_name}-{architecture_name}-{encoder}-{encoder_weights}.pt'
+    model.load_state_dict(torch.hub.load_state_dict_from_url(checkpoint, map_location='cpu'))
+    model.eval()
+    image = preprocess(image)
+    prediction = model(image)
+    prediction = prediction[0, 0].detach().numpy()
+    prediction = prediction > 0.5
+    fig, ax = plt.subplots()
+    ax.tick_params(labelbottom=False, labelleft=False)
+    plt.imshow(image[0, 0], cmap='gray', vmin=-1.5, vmax=1.5)
+    plt.imshow(prediction, cmap='Reds', alpha=0.5)
+    return plt
+
+
+if __name__ == '__main__':
+    experiment_list = ['Lung segmentation', 'Lesion segmentation A']
+    experiment_name_list = [experiment.lower().replace(' ', '-') for experiment in experiment_list]
+    architecture_list = [Unet, Linknet, FPN, PSPNet]
+    architecture_name_list = [architecture.__name__ for architecture in architecture_list]
[…]

### 2022-03-21 ms.tex
Makefile major change

@@
 \begin{document}
-\DTLloaddb{keys-values}{tmp/keys-values.csv}
+\DTLloaddb{keys-values}{artifacts/keys-values.csv}
 
@@
 	\begin{tikzpicture}[]
-		\node[] (input) {\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-image}};
+		\node[] (input) {\includegraphics[scale=0.3]{artifacts/lesion-segmentation-a-image}};
 		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
 		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
-		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-prediction-train-masked-image}};
+		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{artifacts/lesion-segmentation-a-prediction-train-masked-image}};
 		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
-		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-mask-train-masked-image}};
+		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{artifacts/lesion-segmentation-a-mask-train-masked-image}};
 		\node[] at (0, 1){$\bm{X}$};
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{tmp/lung-segmentation-hist}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-a-hist}}
-	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-b-hist}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{artifacts/lung-segmentation-hist}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{artifacts/lesion-segmentation-a-hist}}
+	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{artifacts/lesion-segmentation-b-hist}}
 	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-PSPNet-\worst-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Unet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-PSPNet-\worst-masked-image}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\worst-masked-image}}
-	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\worst-masked-image}}
-	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\worst-masked-image}}
-	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Unet-\worst-masked-image}}
+	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Linknet-\worst-masked-image}}
+	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-FPN-\worst-masked-image}}
+	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-PSPNet-\worst-masked-image}}
 	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{tmp/diff-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{artifacts/diff-scatter-dice-vs-num-parameters}}
 	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{tmp/metrics.tex}
+		\input{artifacts/metrics.tex}
 	\end{adjustbox}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-validation-loss}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-diff-loss}}
-	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-diff-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-train-diff-loss}}
+	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-validation-diff-loss}}
 	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-boxplot-dice}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-boxplot-dice}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-boxplot-dice}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-boxplot-dice}}
-	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{tmp/initialization-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-boxplot-dice}}
+	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{artifacts/initialization-boxplot-dice}}
 	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}\label{fig:box}
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-PSPNet-None-volume}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-PSPNet-None-volume}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-mask--volume}}
-	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Unet-None-volume}}
-	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Linknet-None-volume}}
-	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-FPN-None-volume}}
-	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-mask--volume}}
+	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-Unet-None-volume}}
+	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-Linknet-None-volume}}
+	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-FPN-None-volume}}
+	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-PSPNet-None-volume}}
 	\caption{Reconstructed volumes from predicted masks.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-before-weights}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-None-before-weights}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-None-after-weights}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-before-weights}}
-	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-imagenet-before-weights}}
+	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-imagenet-after-weights}}
 	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.

### 2022-03-21 main.py

@@ -1,6 +1,7 @@
 import glob
 import itertools
 import os
+from os.path import join
 from shutil import rmtree
 from zipfile import ZipFile
 
@@ -24,7 +25,7 @@ from torch import optim
 from torch.utils.data import DataLoader, Dataset
 from torchvision.transforms import functional as tf
 
-tmpdir = os.getenv('TMPDIR')
+artifacts_dir = os.getenv('ARTIFACTSDIR')
 full = os.getenv('FULL')
 plt.rcParams['image.interpolation'] = 'none'
 plt.rcParams['savefig.format'] = 'pdf'
@@ -33,16 +34,16 @@ eps = 1e-6
 
 
 def save_tfjs_from_torch(model, model_name, input_shape):
-    model_name_dir = f'{tmpdir}/tfjs-models/{model_name}'
+    model_name_dir = join(artifacts_dir, 'tfjs-models', model_name)
     os.makedirs(model_name_dir, exist_ok=True)
     example_input = torch.randn(*input_shape, requires_grad=False)
-    torch.onnx.export(model.cpu(), example_input, f'{model_name_dir}/model.onnx', export_params=True, opset_version=11)
-    onnx_model = onnx.load(f'{model_name_dir}/model.onnx')
+    torch.onnx.export(model.cpu(), example_input, join(model_name_dir, 'model.onnx'), export_params=True, opset_version=11)
+    onnx_model = onnx.load(join(model_name_dir, 'model.onnx'))
     tf_model = prepare(onnx_model)
-    tf_model.export_graph(f'{model_name_dir}/model')
-    tf_saved_model_conversion_v2.convert_tf_saved_model(f'{model_name_dir}/model', model_name_dir, skip_op_check=True)
-    rmtree(f'{model_name_dir}/model')
-    os.remove(f'{model_name_dir}/model.onnx')
+    tf_model.export_graph(join(model_name_dir, 'model'))
+    tf_saved_model_conversion_v2.convert_tf_saved_model(join(model_name_dir, 'model'), model_name_dir, skip_op_check=True)
+    rmtree(join(model_name_dir, 'model'))
+    os.remove(join(model_name_dir, 'model.onnx'))
 
 
 def save_figure_weights(model, experiment_name, architecture_name, encoder_weights):
@@ -57,7 +58,7 @@ def save_figure_weights(model, experiment_name, architecture_name, encoder_weigh
[…]

### 2022-04-21 ms.tex
fix names

@@
 	Three experimental setups are conducted for lung segmentation, lesion segmentation and lesion segmentation using the original lung masks.
-	A COVID-19 dataset with $100$ CT scan images is used for training/validation and a different dataset consisting of $\DTLfetch{keys-values}{key}{num-slices-test}{value}$ images from $9$ CT scan volumes for testing.
+	A COVID-19 dataset with $100$ CT scan images is used for training/validation and a different dataset consisting of $\DTLfetch{keys-values}{key}{test-slices-num}{value}$ images from $9$ CT scan volumes for testing.
 	Multiple findings are provided including the best architecture-encoder models for each experiment as well as mean Dice results for each experiment, architecture and encoder independently.
@@
 The original dataset, without the annotations, was selected from the Italian Society of Medical and Interventional Radiology\footnote{\url{https://www.sirm.org/category/senza-categoria/covid-19/}}.
-The second dataset\footnote{\url{https://radiopaedia.org/articles/covid-19-3}} consists of $\DTLfetch{keys-values}{key}{num-slices-test}{value}$ images from $9$ CT\@ scan volumes (a set of CT scan images acquired from the same patient at the same moment) with corresponding target masks.
-373 out of $\DTLfetch{keys-values}{key}{num-slices-test}{value}$ were annotated as positive and segmented by a radiologist by the same group as the first dataset.
+The second dataset\footnote{\url{https://radiopaedia.org/articles/covid-19-3}} consists of $\DTLfetch{keys-values}{key}{test-slices-num}{value}$ images from $9$ CT\@ scan volumes (a set of CT scan images acquired from the same patient at the same moment) with corresponding target masks.
+373 out of $\DTLfetch{keys-values}{key}{test-slices-num}{value}$ were annotated as positive and segmented by a radiologist by the same group as the first dataset.
 Raw data from both datasets contain samples in Hounsfield units~\cite{schneider1996calibration}.
@@
 
-We train a total of $600$ different models for the three experiments each one for $\DTLfetch{keys-values}{key}{num-epochs}{value}$ epochs with a batch size of $\DTLfetch{keys-values}{key}{batch-size}{value}$, which was the maximum possible considering the GPU memory restriction.
+We train a total of $600$ different models for the three experiments each one for $\DTLfetch{keys-values}{key}{epochs-num}{value}$ epochs with a batch size of $\DTLfetch{keys-values}{key}{batch-size}{value}$, which was the maximum possible considering the GPU memory restriction.
 We use the optimizer~\cite{kingma2014adam} with the default values of learning rate $0.001$, $\beta_1=0.9$, $\beta_2=0.999$, $\epsilon=10^{-8}$, without weight decay.

### 2022-04-21 main.py

@@ -28,31 +28,31 @@ from torchvision.transforms import functional as tf
 
 class CTSegBenchmark(Dataset):
     def __init__(self, artifacts_dir, index_range, use_transforms):
-        urls = ['https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1', 'https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1', 'https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1']
-        files = ['COVID-19-CT-Seg_20cases', 'Infection_Mask', 'Lung_Mask']
-        for url, file in zip(urls, files):
-            zip_file = join(artifacts_dir, f'{file}.zip')
-            if not os.path.isfile(zip_file):
+        url_list = ['https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1', 'https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1', 'https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1']
+        file_name_list = ['COVID-19-CT-Seg_20cases', 'Infection_Mask', 'Lung_Mask']
+        for url, file_name in zip(url_list, file_name_list):
+            zip_file_path = join(artifacts_dir, f'{file_name}.zip')
+            if not os.path.isfile(zip_file_path):
                 r = requests.get(url)
-                with open(zip_file, 'wb') as f:
+                with open(zip_file_path, 'wb') as f:
                     f.write(r.content)
-                with ZipFile(zip_file, 'r') as z:
-                    z.extractall(join(artifacts_dir, file))
+                with ZipFile(zip_file_path, 'r') as z:
+                    z.extractall(join(artifacts_dir, file_name))
         images = np.array([]).reshape(512, 512, 0)
-        for fullname in glob.glob(join(artifacts_dir, files[0], '*.nii.gz')):
-            images_ = nib.load(fullname)
+        for file_path in glob.glob(join(artifacts_dir, file_name_list[0], '*.nii.gz')):
+            images_ = nib.load(file_path)
             images_ = np.resize(images_.get_fdata(), (512, 512, images_.shape[-1]))
             images = np.concatenate((images, images_), 2)
         self.images = images[..., index_range]
[…]

### 2022-05-16 python/main.py
major changes

@@ -1,6 +1,7 @@
 from matplotlib import gridspec, pyplot as plt
 from matplotlib.ticker import MaxNLocator
 from onnx_tf.backend import prepare
+from os import environ
 from os.path import join
 from scipy.stats import gaussian_kde
 from segmentation_models_pytorch import FPN, Linknet, PSPNet, Unet
@@ -142,8 +143,8 @@ def calculate_metrics(prediction, mask):
 
 
 def main():
-    artifacts_dir = os.getenv('ARTIFACTSDIR')
-    full = os.getenv('FULL')
+    artifacts_dir = environ['ARTIFACTSDIR']
+    full = environ['FULL']
     plt.rcParams['image.interpolation'] = 'none'
     plt.rcParams['savefig.format'] = 'pdf'
     plt.rcParams['savefig.bbox'] = 'tight'

### 2022-05-16 script.js

@@ -11,7 +11,7 @@ let image = new Image();
 let model;
 
 image.crossOrigin = 'anonymous';
-image.src = 'https://raw.githubusercontent.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/main/docs/lung-segmentation-example-data.png';
+image.src = 'python/release/lung-segmentation-example-data.png';
 
 
 function disableUI(argument) {

### 2022-05-16 ms.tex
fix

--- 2021-08-31 ms.tex
@@
 \usepackage[caption=false,font=footnotesize]{subfig}
+\usepackage[nopdftrailerid=true]{pdfprivacy}
 \usepackage{amssymb}
@@
 \begin{document}
-\DTLloaddb{keys-values}{tmp/keys-values.csv}
+\DTLloaddb{keys-values}{python/artifacts/keys-values.csv}
 
@@
 	\begin{tikzpicture}[]
-		\node[] (input) {\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-image}};
+		\node[] (input) {\includegraphics[scale=0.3]{python/artifacts/lesion-segmentation-a-image}};
 		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
 		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
-		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-prediction-train-masked-image}};
+		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{python/artifacts/lesion-segmentation-a-prediction-train-masked-image}};
 		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
-		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-mask-train-masked-image}};
+		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{python/artifacts/lesion-segmentation-a-mask-train-masked-image}};
 		\node[] at (0, 1){$\bm{X}$};
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{tmp/lung-segmentation-hist}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-a-hist}}
-	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-b-hist}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{python/artifacts/lung-segmentation-hist}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{python/artifacts/lesion-segmentation-a-hist}}
+	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{python/artifacts/lesion-segmentation-b-hist}}
 	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lung-segmentation-PSPNet-\worst-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-Unet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-a-PSPNet-\worst-masked-image}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\worst-masked-image}}
-	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\worst-masked-image}}
-	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\worst-masked-image}}
-	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-Unet-\worst-masked-image}}
+	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-Linknet-\worst-masked-image}}
+	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-FPN-\worst-masked-image}}
+	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{python/artifacts/lesion-segmentation-b-PSPNet-\worst-masked-image}}
 	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{tmp/diff-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{python/artifacts/diff-scatter-dice-vs-num-parameters}}
 	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{tmp/metrics.tex}
+		\input{python/artifacts/metrics.tex}
 	\end{adjustbox}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-a-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-a-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-b-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-b-validation-loss}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-diff-loss}}
-	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-diff-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-b-train-diff-loss}}
+	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-b-validation-diff-loss}}
 	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-boxplot-dice}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-boxplot-dice}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-a-boxplot-dice}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-boxplot-dice}}
-	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{tmp/initialization-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/artifacts/lesion-segmentation-b-boxplot-dice}}
+	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{python/artifacts/initialization-boxplot-dice}}
 	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}\label{fig:box}
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lung-segmentation-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lung-segmentation-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lung-segmentation-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lung-segmentation-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lung-segmentation-PSPNet-None-volume}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-a-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-a-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-a-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-a-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-a-PSPNet-None-volume}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-mask--volume}}
-	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Unet-None-volume}}
-	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Linknet-None-volume}}
-	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-FPN-None-volume}}
-	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-b-mask--volume}}
+	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-b-Unet-None-volume}}
+	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-b-Linknet-None-volume}}
+	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-b-FPN-None-volume}}
+	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{python/artifacts/lesion-segmentation-b-PSPNet-None-volume}}
 	\caption{Reconstructed volumes from predicted masks.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-before-weights}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-Unet-None-before-weights}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-Unet-None-after-weights}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-before-weights}}
-	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-Unet-imagenet-before-weights}}
+	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{python/artifacts/lung-segmentation-Unet-imagenet-after-weights}}
 	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.

### 2022-05-17 python/main.py
apply source_normalizer

@@ -6,7 +6,7 @@ from os.path import join
 from scipy.stats import gaussian_kde
 from segmentation_models_pytorch import FPN, Linknet, PSPNet, Unet
 from segmentation_models_pytorch.utils.losses import DiceLoss
-from shutil import rmtree
+from shutil import move, rmtree
 from skimage.measure import marching_cubes
 from tensorflowjs.converters import tf_saved_model_conversion_v2
 from torch import optim
@@ -28,8 +28,8 @@ import torch
 class CTSegBenchmark(Dataset):
 
     def __getitem__(self, index):
-        (image, lung_mask, lesion_mask) = preprocess_image(self.images[..., index], self.lung_masks[..., index], self.lesion_masks[..., index], self.use_transforms)
-        return (image, lung_mask, lesion_mask)
+        (image, mask_lung, mask_lesion) = preprocess_image(self.images[..., index], self.mask_lesions[..., index], self.mask_lungs[..., index], self.use_transforms)
+        return (image, mask_lung, mask_lesion)
 
     def __init__(self, artifacts_dir, index_range, use_transforms):
         url_list = ['https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1', 'https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1', 'https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1']
@@ -48,18 +48,18 @@ class CTSegBenchmark(Dataset):
             images_ = np.resize(images_.get_fdata(), (512, 512, images_.shape[-1]))
             images = np.concatenate((images, images_), 2)
         self.images = images[..., index_range]
-        lesion_masks = np.array([]).reshape(512, 512, 0)
+        mask_lesions = np.array([]).reshape(512, 512, 0)
         for file_path in glob.glob(join(artifacts_dir, file_name_list[1], '*.nii.gz')):
-            lesion_masks_ = nib.load(file_path)
-            lesion_masks_ = np.resize(lesion_masks_.get_fdata(), (512, 512, lesion_masks_.shape[-1]))
-            lesion_masks = np.concatenate((lesion_masks, lesion_masks_), 2)
-        self.lesion_masks = lesion_masks[..., index_range]
-        lung_masks = np.array([]).reshape(512, 512, 0)
+            mask_lesions_ = nib.load(file_path)
[…]

### 2022-10-06 ms.tex
fix

--- 2022-04-21 ms.tex
@@
 \begin{document}
-\DTLloaddb{keys-values}{artifacts/keys-values.csv}
+\DTLloaddb{keys-values}{python/bin/keys-values.csv}
 
@@
 	\begin{tikzpicture}[]
-		\node[] (input) {\includegraphics[scale=0.3]{artifacts/lesion-segmentation-a-image}};
+		\node[] (input) {\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-image}};
 		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
 		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
-		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{artifacts/lesion-segmentation-a-prediction-train-masked-image}};
+		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-prediction-train-masked-image}};
 		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
-		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{artifacts/lesion-segmentation-a-mask-train-masked-image}};
+		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-mask-train-masked-image}};
 		\node[] at (0, 1){$\bm{X}$};
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{artifacts/lung-segmentation-hist}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{artifacts/lesion-segmentation-a-hist}}
-	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{artifacts/lesion-segmentation-b-hist}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{python/bin/lung-segmentation-hist}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-a-hist}}
+	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-b-hist}}
 	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\best-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lung-segmentation-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\worst-masked-image}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Unet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-a-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\worst-masked-image}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\worst-masked-image}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Unet-\worst-masked-image}}
-	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-Linknet-\worst-masked-image}}
-	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-FPN-\worst-masked-image}}
-	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{artifacts/lesion-segmentation-b-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\worst-masked-image}}
+	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\worst-masked-image}}
+	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\worst-masked-image}}
+	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\worst-masked-image}}
 	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{artifacts/diff-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
+	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{python/bin/diff-scatter-dice-vs-num-parameters}}
 	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{artifacts/metrics.tex}
+		\input{python/bin/metrics.tex}
 	\end{adjustbox}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-validation-loss}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-loss}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-loss}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-train-diff-loss}}
-	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-validation-diff-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-diff-loss}}
+	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-diff-loss}}
 	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-boxplot-dice}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-a-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-boxplot-dice}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-boxplot-dice}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{artifacts/lesion-segmentation-b-boxplot-dice}}
-	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{artifacts/initialization-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-boxplot-dice}}
+	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{python/bin/initialization-boxplot-dice}}
 	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}\label{fig:box}
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lung-segmentation-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-PSPNet-None-volume}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-mask--volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-a-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-mask--volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Unet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Linknet-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-FPN-None-volume}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-PSPNet-None-volume}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-mask--volume}}
-	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-Unet-None-volume}}
-	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-Linknet-None-volume}}
-	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-FPN-None-volume}}
-	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{artifacts/lesion-segmentation-b-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-mask--volume}}
+	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Unet-None-volume}}
+	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Linknet-None-volume}}
+	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-FPN-None-volume}}
+	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-PSPNet-None-volume}}
 	\caption{Reconstructed volumes from predicted masks.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-None-before-weights}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-None-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-before-weights}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-after-weights}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-imagenet-before-weights}}
-	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{artifacts/lung-segmentation-Unet-imagenet-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-before-weights}}
+	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-after-weights}}
 	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.

### 2022-10-06 python/main.py

@@ -31,31 +31,31 @@ class CTSegBenchmark(Dataset):
         (image, mask_lung, mask_lesion) = preprocess_image(self.images[..., index], self.mask_lesions[..., index], self.mask_lungs[..., index], self.use_transforms)
         return (image, mask_lung, mask_lesion)
 
-    def __init__(self, artifacts_dir, index_range, use_transforms):
+    def __init__(self, index_range, use_transforms):
         url_list = ['https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1', 'https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1', 'https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1']
         file_name_list = ['COVID-19-CT-Seg_20cases', 'Infection_Mask', 'Lung_Mask']
         for (url, file_name) in zip(url_list, file_name_list):
-            zip_file_path = join(artifacts_dir, f'{file_name}.zip')
+            zip_file_path = join('bin', f'{file_name}.zip')
             if not os.path.isfile(zip_file_path):
                 response = requests.get(url)
                 with open(zip_file_path, 'wb') as file:
                     file.write(response.content)
                 with ZipFile(zip_file_path, 'r') as zip_file:
-                    zip_file.extractall(join(artifacts_dir, file_name))
+                    zip_file.extractall(join('bin', file_name))
         images = np.array([]).reshape(512, 512, 0)
-        for file_path in glob.glob(join(artifacts_dir, file_name_list[0], '*.nii.gz')):
+        for file_path in glob.glob(join('bin', file_name_list[0], '*.nii.gz')):
             images_ = nib.load(file_path)
             images_ = np.resize(images_.get_fdata(), (512, 512, images_.shape[-1]))
             images = np.concatenate((images, images_), 2)
         self.images = images[..., index_range]
         mask_lesions = np.array([]).reshape(512, 512, 0)
-        for file_path in glob.glob(join(artifacts_dir, file_name_list[1], '*.nii.gz')):
+        for file_path in glob.glob(join('bin', file_name_list[1], '*.nii.gz')):
             mask_lesions_ = nib.load(file_path)
             mask_lesions_ = np.resize(mask_lesions_.get_fdata(), (512, 512, mask_lesions_.shape[-1]))
             mask_lesions = np.concatenate((mask_lesions, mask_lesions_), 2)
         self.mask_lesions = mask_lesions[..., index_range]
[…]

### 2022-10-06 script.js

@@ -9,7 +9,7 @@ let image = new Image();
 let model;
 
 image.crossOrigin = 'anonymous';
-image.src = 'python/release/lung-segmentation-example-data.png';
+image.src = 'python/dist/lung-segmentation-example-data.png';
 
 
 function disableUI(argument) {

### 2022-10-31 python/main.py
fix

@@ -151,7 +151,7 @@ def main():
     range_validation = range(80, 100)
     range_test_volume = range(9)
     encoder_name_list = ['vgg11', 'vgg13', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201', 'resnext50_32x4d', 'dpn68', 'dpn98', 'mobilenet_v2', 'xception', 'inceptionv4', 'efficientnet-b0', 'efficientnet-b1', 'efficientnet-b2', 'efficientnet-b3', 'efficientnet-b4', 'efficientnet-b5', 'efficientnet-b6']
-    if environ['debug'] == '1':
+    if environ['DEBUG'] == '1':
         epochs_num = 2
         range_training = range(1)
         range_validation = range(2, 4)
@@ -320,10 +320,10 @@ def main():
                     model_file_name = f'{experiment_name}.{architecture_name}.{encoder_name}.{encoder_weights}'
                     if model_file_name in ['lesion-segmentation-a.FPN.mobilenet_v2.imagenet', 'lung-segmentation.FPN.mobilenet_v2.imagenet']:
                         save_tfjs_from_torch(dataset_training[0][0].unsqueeze(0), model, model_file_name)
-                        if environ['debug'] != '1':
+                        if environ['DEBUG'] != '1':
                             rmtree(join('dist', model_file_name))
                             move(join('bin', model_file_name), join('dist', model_file_name))
-                    if environ['debug'] == '1':
+                    if environ['DEBUG'] == '1':
                         os.remove(model_file_path)
     for (hist_images, hist_masks, experiment_name) in zip(hist_images_array, hist_masks_array, experiment_name_list):
         save_figure_histogram(experiment_name, hist_images, hist_masks, hist_range)
@@ -411,7 +411,7 @@ def preprocess_image(image, mask_lesion, mask_lung, use_transforms):
 
 
 def save_figure_3d(architecture, encoder_weights, experiment_name, volume):
-    if environ['debug'] == '1':
+    if environ['DEBUG'] == '1':
         step_size = 10
     else:
         step_size = 1
@@ -579,7 +579,9 @@ def save_figure_weights(architecture_name, encoder_weights, experiment_name, mod
 
 def save_tfjs_from_torch(example_input, model, model_file_name):
     model_file_path = join('bin', model_file_name)
[…]

### 2022-11-03 python/main.py
fix

@@ -1,3 +1,4 @@
+from fvcore.nn import FlopCountAnalysis
 from matplotlib import gridspec, pyplot as plt
 from matplotlib.ticker import MaxNLocator
 from onnx_tf.backend import prepare
@@ -183,8 +184,7 @@ def main():
     hist_masks_array = np.zeros_like(hist_images_array)
     loss_training_array = np.zeros((len(experiment_list), len(architecture_list), len(encoder_name_list), len(encoder_weights_list), epochs_num))
     loss_validation_array = np.zeros_like(loss_training_array)
-    training_time_array = np.zeros((len(experiment_list), len(architecture_list), len(encoder_name_list), len(encoder_weights_list)))
-    validation_time_array = np.zeros_like(training_time_array)
+    flops_array = np.zeros((len(experiment_list), len(architecture_list), len(encoder_name_list), len(encoder_weights_list)))
     for (experiment_name_index, experiment_name) in enumerate(experiment_name_list):
         for (architecture_index, (architecture, architecture_name)) in enumerate(zip(architecture_list, architecture_name_list)):
             for (encoder_name_index, encoder_name) in enumerate(encoder_name_list):
@@ -194,6 +194,8 @@ def main():
                     optimizer = optim.Adam(model.parameters())
                     loss_validation_best = float('inf')
                     model_file_path = join('bin', f'{experiment_name}-{architecture_name}-{encoder_name}-{encoder_weights}.pt')
+                    flops = FlopCountAnalysis(model, dataloader_training.dataset[0][0].unsqueeze(0).to(device))
+                    flops_array[experiment_name_index, architecture_index, encoder_name_index, encoder_weights_index] = flops.total()
                     for (epoch_index, epoch) in enumerate(range(epochs_num)):
                         loss_training_sum = 0
                         model.train()
@@ -207,14 +209,7 @@ def main():
                                 masks = mask_lesions
                             images = images.to(device)
                             masks = masks.to(device)
-                            if device == 'cuda':
-                                with torch.autograd.profiler.profile(use_cuda=True) as prof:
-                                    predictions = model(images)
-                                training_time_array[experiment_name_index, architecture_index, encoder_name_index, encoder_weights_index] += sum((item.cuda_time for item in prof.function_events))
-                            else:
[…]

### 2022-11-03 python/main.py
fix

@@ -29,13 +29,13 @@ import torch
 class CTSegBenchmark(Dataset):
 
     def __getitem__(self, index):
-        (image, mask_lung, mask_lesion) = preprocess_image(self.images[..., index], self.mask_lesions[..., index], self.mask_lungs[..., index], self.use_transforms)
+        image, mask_lung, mask_lesion = preprocess_image(self.images[..., index], self.mask_lesions[..., index], self.mask_lungs[..., index], self.use_transforms)
         return (image, mask_lung, mask_lesion)
 
     def __init__(self, index_range, use_transforms):
         url_list = ['https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1', 'https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1', 'https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1']
         file_name_list = ['COVID-19-CT-Seg_20cases', 'Infection_Mask', 'Lung_Mask']
-        for (url, file_name) in zip(url_list, file_name_list):
+        for url, file_name in zip(url_list, file_name_list):
             zip_file_path = join('bin', f'{file_name}.zip')
             if not os.path.isfile(zip_file_path):
                 response = requests.get(url)
@@ -70,13 +70,13 @@ class CTSegBenchmark(Dataset):
 class MedicalSegmentation1(Dataset):
 
     def __getitem__(self, index):
-        (image, mask_lung, mask_lesion) = preprocess_image(self.images[..., index], self.mask_lesions[..., index], self.mask_lungs[..., index], self.use_transforms)
+        image, mask_lung, mask_lesion = preprocess_image(self.images[..., index], self.mask_lesions[..., index], self.mask_lungs[..., index], self.use_transforms)
         return (image, mask_lung, mask_lesion)
 
     def __init__(self, index_range, use_transforms):
         url_list = ['https://drive.google.com/uc?id=1SJoMelgRqb0EuqlTuq6dxBWf2j9Kno8S', 'https://drive.google.com/uc?id=1MEqpbpwXjrLrH42DqDygWeSkDq0bi92f', 'https://drive.google.com/uc?id=1zj4N_KV0LBko1VSQ7FPZ38eaEGNU0K6-']
         file_name_list = ['tr_im.nii.gz', 'tr_mask.nii.gz', 'tr_lungmasks_updated.nii.gz']
-        for (url, file_name) in zip(url_list, file_name_list):
[…]

### 2023-01-17 ms.tex
fix

@@
 Regarding preprocessing, first the positive classes of the pixels of the images in the first dataset are merged into one, converting the problem to a binary segmentation problem.
-The CT scan images from the second dataset are resized to $512\times 512$, and both datasets are normalized with $\mu=-500$ and $\sigma=500$.
+The CT scan images from the second dataset are resized to $512\times 512$, and for both datasets pixel values are divided with $4095$.
 We use $80$ scans from the first dataset for training the models, $20$ scans for validation and all scans from the second dataset for the testing of the models.
@@
 The best combination of architecture-encoder for each combination of encoder weight initialization, experimental setup and metric are showin in bold.
-The mean Dice results for each experiment are $\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-std}{value}\%$, for `lesion segmentation A' and $\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-std}{value}\%$, for `lesion segmentation B'.
+The mean Dice results for each experiment are $\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-mean}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-mean}{value}\%$, for `lesion segmentation A' and $\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-mean}{value}\%$, for `lesion segmentation B'.
 The best performing models w.r.t.\ Dice for each experiment were the \DTLfetch{keys-values}{key}{lung-segmentation-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lung-segmentation-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-max}{value}\%$) for lung segmentation, \DTLfetch{keys-values}{key}{lesion-segmentation-a-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lesion-segmentation-a-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-max}{value}\%$) for lesion segmentation A and \DTLfetch{keys-values}{key}{lesion-segmentation-b-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lesion-segmentation-b-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-max}{value}\%$) for lesion segmentation B.
@@
 
-The mean Dice results for Unet are $\DTLfetch{keys-values}{key}{lung-segmentation-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-Unet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-Unet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-Unet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-Unet-imagenet-std}{value}\%$ for `lesion segmentation B'.
-The mean Dice results for Linknet are $\DTLfetch{keys-values}{key}{lung-segmentation-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-Linknet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-Linknet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-Linknet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-Linknet-imagenet-std}{value}\%$ for `lesion segmentation B'.
-The mean Dice results for FPN are $\DTLfetch{keys-values}{key}{lung-segmentation-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-FPN-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-FPN-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-FPN-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-FPN-imagenet-std}{value}\%$ for `lesion segmentation B'.
-The mean Dice results for PSPNet are $\DTLfetch{keys-values}{key}{lung-segmentation-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lung-segmentation-PSPNet-imagenet-std}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-a-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-PSPNet-imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{lesion-segmentation-b-PSPNet-imagenet-std}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for Unet are $\DTLfetch{keys-values}{key}{lung-segmentation-Unet-imagenet-mean}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-Unet-imagenet-mean}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-Unet-imagenet-mean}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for Linknet are $\DTLfetch{keys-values}{key}{lung-segmentation-Linknet-imagenet-mean}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-Linknet-imagenet-mean}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-Linknet-imagenet-mean}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for FPN are $\DTLfetch{keys-values}{key}{lung-segmentation-FPN-imagenet-mean}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-FPN-imagenet-mean}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-FPN-imagenet-mean}{value}\%$ for `lesion segmentation B'.
+The mean Dice results for PSPNet are $\DTLfetch{keys-values}{key}{lung-segmentation-PSPNet-imagenet-mean}{value}\%$ for lung segmentation, $\DTLfetch{keys-values}{key}{lesion-segmentation-a-PSPNet-imagenet-mean}{value}\%$ for `lesion segmentation A', $\DTLfetch{keys-values}{key}{lesion-segmentation-b-PSPNet-imagenet-mean}{value}\%$ for `lesion segmentation B'.
 
@@
 In Fig.~\ref{fig:weights} the weights are depicted, in which we observe that with random initialization the weights depict high and low frequency textures after training.
-The Dice for using random initialization is $\DTLfetch{keys-values}{key}{None-mean}{value}\%\pm\DTLfetch{keys-values}{key}{None-std}{value}\%$ and for ImageNet initialization is $\DTLfetch{keys-values}{key}{imagenet-mean}{value}\%\pm\DTLfetch{keys-values}{key}{imagenet-std}{value}\%$.
+The Dice for using random initialization is $\DTLfetch{keys-values}{key}{None-mean}{value}\%$ and for ImageNet initialization is $\DTLfetch{keys-values}{key}{imagenet-mean}{value}\%$.
 

### 2023-01-17 python/main.py

@@ -38,7 +38,7 @@ class CTSegBenchmark(Dataset):
     def __init__(self, index_range, use_transforms):
         url_list = ['https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1', 'https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1', 'https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1']
         file_name_list = ['COVID-19-CT-Seg_20cases', 'Infection_Mask', 'Lung_Mask']
-        for url, file_name in zip(url_list, file_name_list, strict=True):
+        for url, file_name in zip(url_list, file_name_list):
             zip_file_path = join('bin', f'{file_name}.zip')
             if not os.path.isfile(zip_file_path):
                 response = requests.get(url, timeout=5)
@@ -79,7 +79,7 @@ class MedicalSegmentation1(Dataset):
     def __init__(self, index_range, use_transforms):
         url_list = ['https://drive.google.com/uc?id=1SJoMelgRqb0EuqlTuq6dxBWf2j9Kno8S', 'https://drive.google.com/uc?id=1MEqpbpwXjrLrH42DqDygWeSkDq0bi92f', 'https://drive.google.com/uc?id=1zj4N_KV0LBko1VSQ7FPZ38eaEGNU0K6-']
         file_name_list = ['tr_im.nii.gz', 'tr_mask.nii.gz', 'tr_lungmasks_updated.nii.gz']
-        for url, file_name in zip(url_list, file_name_list, strict=True):
+        for url, file_name in zip(url_list, file_name_list):
             if not os.path.isfile(join('bin', file_name)):
                 gdown.download(url, join('bin', file_name), quiet=False)
         images_file_path = join('bin', 'tr_im.nii.gz')
@@ -106,7 +106,7 @@ class MedicalSegmentation2(Dataset):
     def __init__(self, index_volume, use_transforms):
         url_list = ['https://drive.google.com/uc?id=1ruTiKdmqhqdbE9xOEmjQGing76nrTK2m', 'https://drive.google.com/uc?id=1gVuDwFeAGa6jIVX9MeJV5ByIHFpOo5Bp', 'https://drive.google.com/uc?id=1MIp89YhuAKh4as2v_5DUoExgt6-y3AnH']
         file_name_list = ['rp_im.zip', 'rp_msk.zip', 'rp_lung_msk.zip']
-        for url, file_name in zip(url_list, file_name_list, strict=True):
[…]

### 2023-01-17 python/main.py
fix

@@ -3,7 +3,7 @@ import itertools
 import os
 import ssl
 from os import environ
-from os.path import join
+from os.path import isfile, join
 from shutil import move, rmtree
 from zipfile import ZipFile
 
@@ -40,8 +40,8 @@ class CTSegBenchmark(Dataset):
         file_name_list = ['COVID-19-CT-Seg_20cases', 'Infection_Mask', 'Lung_Mask']
         for url, file_name in zip(url_list, file_name_list):
             zip_file_path = join('bin', f'{file_name}.zip')
-            if not os.path.isfile(zip_file_path):
-                response = requests.get(url, timeout=5)
+            if not isfile(zip_file_path):
+                response = requests.get(url, timeout=60)
                 with open(zip_file_path, 'wb') as file:
                     file.write(response.content)
                 with ZipFile(zip_file_path, 'r') as zip_file:
@@ -80,7 +80,7 @@ class MedicalSegmentation1(Dataset):
         url_list = ['https://drive.google.com/uc?id=1SJoMelgRqb0EuqlTuq6dxBWf2j9Kno8S', 'https://drive.google.com/uc?id=1MEqpbpwXjrLrH42DqDygWeSkDq0bi92f', 'https://drive.google.com/uc?id=1zj4N_KV0LBko1VSQ7FPZ38eaEGNU0K6-']
         file_name_list = ['tr_im.nii.gz', 'tr_mask.nii.gz', 'tr_lungmasks_updated.nii.gz']
         for url, file_name in zip(url_list, file_name_list):
-            if not os.path.isfile(join('bin', file_name)):
+            if not isfile(join('bin', file_name)):
                 gdown.download(url, join('bin', file_name), quiet=False)
         images_file_path = join('bin', 'tr_im.nii.gz')
         images = nib.load(images_file_path)
@@ -108,7 +108,7 @@ class MedicalSegmentation2(Dataset):
         file_name_list = ['rp_im.zip', 'rp_msk.zip', 'rp_lung_msk.zip']
         for url, file_name in zip(url_list, file_name_list):
             zip_file_path = join('bin', file_name)
-            if not os.path.isfile(zip_file_path):
+            if not isfile(zip_file_path):
                 gdown.download(url, zip_file_path, quiet=False)
                 with ZipFile(zip_file_path, 'r') as zip_file:
                     zip_file.extractall('bin')

### 2023-01-18 python/main.py
fix

@@ -3,7 +3,7 @@ import itertools
 import os
 import ssl
 from os import environ
-from os.path import isfile, join
+from os.path import exists, isfile, join
 from shutil import move, rmtree
 from zipfile import ZipFile
 
@@ -550,7 +550,7 @@ def save_figure_weights(architecture_name, encoder_weights, experiment_name, mod
 
 def save_tfjs_from_torch(example_input, model, model_file_name):
     model_file_path = join('bin', model_file_name)
-    if os.path.exists(model_file_path):
+    if exists(model_file_path):
         rmtree(model_file_path)
     os.makedirs(model_file_path)
     torch.onnx.export(model.cpu(), example_input, join(model_file_path, 'model.onnx'), export_params=True, opset_version=16)

### 2023-01-19 python/main.py
fix

@@ -322,7 +322,7 @@ def main():
         save_figure_scatter(architecture_name_list, metrics_[..., -1], experiment_name, parameters_num_array, [70, 100])
     save_figure_scatter(architecture_name_list, metrics_array[2, ..., -1] - metrics_array[1, ..., -1], 'diff', parameters_num_array, [-15, 15])
     save_figure_initialization_box(metrics_array[..., -1], encoder_weights_list)
-    encoder_weights_mean = metrics_array[..., -1].reshape(-1, len(encoder_weights_list)).mean(0).round(2)
+    encoder_weights_mean = metrics_array[..., -1].reshape(-1, len(encoder_weights_list)).mean(0).round(1)
     encoder_mean = metrics_array.transpose([2, 0, 1, 3, 4]).reshape(metrics_array.shape[2], -1).mean(1)
     metrics_array = metrics_array.transpose([1, 2, 3, 0, 4])
     metrics_array_global_mean = metrics_array.reshape(-1, np.prod(metrics_array.shape[2:])).mean(0)
@@ -341,11 +341,11 @@ def main():
     metrics_df['Performance', 'related', 'FLOPS(B)'] = flops_array.flatten()
     metrics_df.loc[('Global', 'Mean'), :] = np.append(metrics_array_global_mean, (parameters_num_array_global_mean, flops_array_global_mean))
     metrics_df.index.names = ['Architecture', 'Encoder']
-    metrics_df = metrics_df.round(2)
+    metrics_df = metrics_df.round(1)
     max_per_column_list = metrics_df.max(0)
     max_per_column_index_list = metrics_df.idxmax(0)
     styler = metrics_df.style
-    styler.format(precision=2)
+    styler.format(precision=1)
     styler.highlight_max(props='bfseries: ;')
     styler.highlight_min(props='bfseries: ;')
     styler.to_latex(join('bin', 'metrics.tex'), hrules=True, multicol_align='c')

### 2023-03-28 ms.tex
.

@@
 \subsection{Formalization}
-Let $\mathcal{D}$ be a dataset containing images $\bm{X} \in \mathbb{R}^{n_r, n_c}$ and $\bm{Y} \in \{0, 1\}^{n_r, n_c}$ the corresponding target mask (in our case $n_r=512$, $n_c=512$).
+Let $\mathcal{D}$ be a dataset containing images $\bm{X} \in \mathbb{R}^{n_r, n_c}$ and $\bm{Y} \in \{0, 1\}^{n_r, n_c}$ the corresponding target mask (in our case $n_r=512$, $n_c=512$). % chktex 3
 Let $m_{ex, ar, en, ew}$ be a DL model for segmentation where $ex$ denotes the specific experiment, $ar$ the architecture, $en$ the encoder and $ew$ the encoder weights.
@@
 The model $m_{ex, ar, en, ew}$ is trained on a dataset $\mathcal{D}_{train}\subset\mathcal{D}$ consisting of $\bm{X}_{train} \in \mathbb{R}^{n_r, n_c}$ and $\bm{Y}_{train} \in \{0, 1\}^{n_r, n_c}$.
+% chktex 3
 Moreover a validation dataset is defined as $\mathcal{D}_{val}\subset\mathcal{D}$ where $\mathcal{D}_{val}\cap\mathcal{D}_{train}=\emptyset$ consisting of $\bm{X}_{val} \in \mathbb{R}^{n_r, n_c}$ and $\bm{Y}_{val} \in \{0, 1\}^{n_r, n_c}$.
+% chktex 3
 Therefore, the objective of the experiments conducted in this study can be designed as, finding an optimal point in the parameter space of $m_{ex, ar, en, ew}$ during training such that when presented with an input from $\mathcal{D}$ such as $\bm{X}_{val}$, its prediction $\hat{\bm{Y}}_{val} \in [0, 1]^{n_r, n_c}$ is as near as possible with the target $\bm{Y}_{val}$.
+% chktex 3
 This is implemented by selecting the model that performs the minimum validation error out of all epochs.
@@
 The second dataset\footnote{\url{https://radiopaedia.org/articles/covid-19-3}} consists of $\DTLfetch{keys-values}{key}{test-slices-num}{value}$ images from $9$ CT\@ scan volumes (a set of CT scan images acquired from the same patient at the same moment) with corresponding target masks.
+% chktex 8
 373 out of $\DTLfetch{keys-values}{key}{test-slices-num}{value}$ were annotated as positive and segmented by a radiologist by the same group as the first dataset.
@@
 		\midrule
-		Linknet & 5 & Yes (decoder) & -                                                                              \\
+		Linknet & 5 & Yes (decoder) & N/A                                                                              \\
 		\midrule
@@
 Pytorch~\cite{paszke2019pytorch} and the `Segmentation Models Pytorch' library~\cite{yakubovskiy2019segmentation} were used for implementing the experiments, a GeForce RTX 2080 Ti Graphics Card with 11Gb RAM from NVIDIA and an Intel Core i9-9900K CPU @3.60GHz, on a Linux-based operating system for training the models for two weeks.
+% chktex 8
 A pseudo-code implementation of the experimental setup is shown in Algorithm~\ref{alg:experimentalsetup}.
@@
 The best performing models w.r.t.\ Dice for each experiment were the \DTLfetch{keys-values}{key}{lung-segmentation-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lung-segmentation-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lung-segmentation-imagenet-max}{value}\%$) for lung segmentation, \DTLfetch{keys-values}{key}{lesion-segmentation-a-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lesion-segmentation-a-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lesion-segmentation-a-imagenet-max}{value}\%$) for lesion segmentation A and \DTLfetch{keys-values}{key}{lesion-segmentation-b-architecture-imagenet-index-max}{value}-\DTLfetch{keys-values}{key}{lesion-segmentation-b-encoder-imagenet-index-max}{value} ($\DTLfetch{keys-values}{key}{lesion-segmentation-b-imagenet-max}{value}\%$) for lesion segmentation B.
+% chktex 35
 In Fig.~\ref{fig:predictedmasks} the predicted masks for $24$ out of the $600$ models are depicted, demonstrating the difference in segmentation quality between the best (\DTLfetch{keys-values}{key}{encoder-best}{value}) and the worst (\DTLfetch{keys-values}{key}{encoder-worst}{value}) performing encoder of the models for each architecture, with randomly initialized weights.
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-mask--volume}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-mask--volume}} % chktex 8
 	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Unet-None-volume}}
@@
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-mask--volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-mask--volume}} % chktex 8
 	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Unet-None-volume}}
@@
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-mask--volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-mask--volume}} % chktex 8
 	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Unet-None-volume}}

### 2023-03-28 python/main.py

@@ -339,8 +339,8 @@ def main() -> None: # noqa: C901, PLR0912, PLR0915
     index = pd.MultiIndex.from_product([architecture_names, [encoder_name.replace("_", "") for encoder_name in encoder_names] + ["Mean"]])
     multicolumn = pd.MultiIndex.from_product([[str(encoder_weights) for encoder_weights in encoders_weights], experiments, metric_names])
     metrics_df = pd.DataFrame(metrics_array, index=index, columns=multicolumn)
-    metrics_df["Performance", "related", "Pars(M)"] = parameters_num_array.flatten()
-    metrics_df["Performance", "related", "FLOPS(B)"] = flops_array.flatten()
+    metrics_df["Performance", "related", "Pars (M)"] = parameters_num_array.flatten()
+    metrics_df["Performance", "related", "FLOPS (B)"] = flops_array.flatten()
     metrics_df.loc[("Global", "Mean"), :] = np.append(metrics_array_global_mean, (parameters_num_array_global_mean, flops_array_global_mean))
     metrics_df.index.names = ["Architecture", "Encoder"]
     metrics_df = metrics_df.round(1)

### 2023-05-11 latex/ms.tex
.

--- 2023-03-28 ms.tex
@@
 	\begin{tikzpicture}[]
-		\node[] (input) {\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-image}};
+		\node[] (input) {\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-image.png}};
 		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
 		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
-		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-prediction-train-masked-image}};
+		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-prediction-train-masked-image.png}};
 		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
-		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-mask-train-masked-image}};
+		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-mask-train-masked-image.png}};
 		\node[] at (0, 1){$\bm{X}$};
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{python/bin/lung-segmentation-hist}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-a-hist}}
-	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-b-hist}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{python/bin/lung-segmentation-hist.png}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-a-hist.png}}
+	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-b-hist.png}}
 	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\best-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\best-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\best-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\worst-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\worst-masked-image.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\worst-masked-image}}
-	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\worst-masked-image}}
-	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\worst-masked-image}}
-	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\worst-masked-image.png}}
+	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\worst-masked-image.png}}
+	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\worst-masked-image.png}}
+	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\worst-masked-image.png}}
 	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-scatter-dice-vs-num-parameters.png}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-scatter-dice-vs-num-parameters.png}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{python/bin/diff-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-scatter-dice-vs-num-parameters.png}}
+	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{python/bin/diff-scatter-dice-vs-num-parameters.png}}
 	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-train-loss.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-validation-loss.png}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-train-loss.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-validation-loss.png}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-loss.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-loss.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-diff-loss}}
-	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-diff-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-diff-loss.png}}
+	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-diff-loss.png}}
 	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-boxplot-dice}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-boxplot-dice.png}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-boxplot-dice.png}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-boxplot-dice}}
-	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{python/bin/initialization-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-boxplot-dice.png}}
+	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{python/bin/initialization-boxplot-dice.png}}
 	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}\label{fig:box}
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-mask--volume}} % chktex 8
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-mask--volume.png}} % chktex 8
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Unet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Linknet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-FPN-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-PSPNet-None-volume.png}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-mask--volume}} % chktex 8
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-mask--volume.png}} % chktex 8
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Unet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Linknet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-FPN-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-PSPNet-None-volume.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-mask--volume}} % chktex 8
-	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Unet-None-volume}}
-	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Linknet-None-volume}}
-	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-FPN-None-volume}}
-	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-mask--volume.png}} % chktex 8
+	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Unet-None-volume.png}}
+	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Linknet-None-volume.png}}
+	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-FPN-None-volume.png}}
+	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-PSPNet-None-volume.png}}
 	\caption{Reconstructed volumes from predicted masks.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-before-weights}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-before-weights.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-after-weights.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-before-weights}}
-	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-before-weights.png}}
+	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-after-weights.png}}
 	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.

### 2023-05-11 latex/python/main.py

@@ -146,7 +146,6 @@ def main() -> None: # noqa: C901, PLR0912, PLR0915
         data_file_path.mkdir(parents=True)
     ssl._create_default_https_context = ssl._create_unverified_context # noqa: SLF001
     plt.rcParams["image.interpolation"] = "none"
-    plt.rcParams["savefig.format"] = "pdf"
     plt.rcParams["savefig.bbox"] = "tight"
     encoder_names = ["vgg11", "vgg13", "vgg19", "resnet18", "resnet34", "resnet50", "resnet101", "resnet152", "densenet121", "densenet161", "densenet169", "densenet201", "resnext50_32x4d", "dpn68", "dpn98", "mobilenet_v2", "xception", "inceptionv4", "efficientnet-b0", "efficientnet-b1", "efficientnet-b2", "efficientnet-b3", "efficientnet-b4", "efficientnet-b5", "efficientnet-b6"]
     epochs_num = 100
@@ -410,7 +409,7 @@ def save_figure_3d(architecture: str, encoder_weights: str | None, experiment_na
         line.set_visible(False) # noqa: FBT003
     for line in ax.zaxis.get_ticklines():
         line.set_visible(False) # noqa: FBT003
-    plt.savefig(f"bin/{experiment_name}-{architecture}-{encoder_weights}-volume")
+    plt.savefig(f"bin/{experiment_name}-{architecture}-{encoder_weights}-volume.png")
     plt.close()
 
 
@@ -421,7 +420,7 @@ def save_figure_architecture_box(architecture_names: list[str], dice: np.ndarray
     plt.grid(visible=True)
     plt.xticks(ticks=np.arange(len(architecture_names)) + 1, labels=architecture_names, fontsize=15)
     plt.ylim([70, 100])
-    plt.savefig(f"bin/{experiment_name}-boxplot-dice")
+    plt.savefig(f"bin/{experiment_name}-boxplot-dice.png")
     plt.close()
 
 
@@ -441,7 +440,7 @@ def save_figure_histogram(experiment_name: str, hist_images: np.ndarray, hist_ma
     plt.grid(visible=True, which="both")
     ax.set_yscale("log")
     ax.legend()
-    plt.savefig(f"bin/{experiment_name}-hist")
+    plt.savefig(f"bin/{experiment_name}-hist.png")
     plt.close()
 
 
[…]

### 2023-06-25 latex/python/main.py
.

@@ -75,21 +75,21 @@ class CTSegBenchmark(Dataset):  # type: ignore[type-arg]
         ]
         file_names = ["COVID-19-CT-Seg_20cases", "Infection_Mask", "Lung_Mask"]
         for url, file_name in zip(urls, file_names, strict=True):
-            zip_file_path = Path("data") / f"{file_name}.zip"
+            zip_file_path = Path("bin") / f"{file_name}.zip"
             if not zip_file_path.is_file():
                 response = requests.get(url, timeout=60)
                 with zip_file_path.open("wb") as file:
                     file.write(response.content)
                 with ZipFile(zip_file_path, "r") as zip_file:
-                    zip_file.extractall(f"data/{file_name}")
+                    zip_file.extractall(f"bin/{file_name}")
         images: np.ndarray = np.array([]).reshape(512, 512, 0)  # type: ignore[type-arg]
-        for file_path in glob.glob(f"data/{file_names[0]}/*.nii.gz"):
+        for file_path in glob.glob(f"bin/{file_names[0]}/*.nii.gz"):
             images_ = nib.load(file_path)  # type: ignore[attr-defined]
             images_ = np.resize(images_.get_fdata(), (512, 512, images_.shape[-1]))
             images = np.concatenate((images, images_), 2)
         self.images = images[..., index_range]
         mask_lesions: np.ndarray = np.array([]).reshape(512, 512, 0)  # type: ignore[type-arg] # noqa: E501
-        for file_path in glob.glob(f"data/{file_names[1]}/*.nii.gz"):
+        for file_path in glob.glob(f"bin/{file_names[1]}/*.nii.gz"):
             mask_lesions_ = nib.load(file_path)  # type: ignore[attr-defined]
             mask_lesions_ = np.resize(
                 mask_lesions_.get_fdata(),
@@ -98,7 +98,7 @@ class CTSegBenchmark(Dataset):  # type: ignore[type-arg]
             mask_lesions = np.concatenate((mask_lesions, mask_lesions_), 2)
         self.mask_lesions = mask_lesions[..., index_range]
         mask_lungs: np.ndarray = np.array([]).reshape(512, 512, 0)  # type: ignore[type-arg] # noqa: E501
-        for file_path in glob.glob(f"data/{file_names[2]}/*.nii.gz"):
+        for file_path in glob.glob(f"bin/{file_names[2]}/*.nii.gz"):
[…]

### 2023-06-27 latex/python/main.py
rename bin to tmp

@@ -75,21 +75,21 @@ class CTSegBenchmark(Dataset):  # type: ignore[type-arg]
         ]
         file_names = ["COVID-19-CT-Seg_20cases", "Infection_Mask", "Lung_Mask"]
         for url, file_name in zip(urls, file_names, strict=True):
-            zip_file_path = Path("bin") / f"{file_name}.zip"
+            zip_file_path = Path("tmp") / f"{file_name}.zip"
             if not zip_file_path.is_file():
                 response = requests.get(url, timeout=60)
                 with zip_file_path.open("wb") as file:
                     file.write(response.content)
                 with ZipFile(zip_file_path, "r") as zip_file:
-                    zip_file.extractall(f"bin/{file_name}")
+                    zip_file.extractall(f"tmp/{file_name}")
         images: np.ndarray = np.array([]).reshape(512, 512, 0)  # type: ignore[type-arg]
-        for file_path in glob.glob(f"bin/{file_names[0]}/*.nii.gz"):
+        for file_path in glob.glob(f"tmp/{file_names[0]}/*.nii.gz"):
             images_ = nib.load(file_path)  # type: ignore[attr-defined]
             images_ = np.resize(images_.get_fdata(), (512, 512, images_.shape[-1]))
             images = np.concatenate((images, images_), 2)
         self.images = images[..., index_range]
         mask_lesions: np.ndarray = np.array([]).reshape(512, 512, 0)  # type: ignore[type-arg] # noqa: E501
-        for file_path in glob.glob(f"bin/{file_names[1]}/*.nii.gz"):
+        for file_path in glob.glob(f"tmp/{file_names[1]}/*.nii.gz"):
             mask_lesions_ = nib.load(file_path)  # type: ignore[attr-defined]
             mask_lesions_ = np.resize(
                 mask_lesions_.get_fdata(),
@@ -98,7 +98,7 @@ class CTSegBenchmark(Dataset):  # type: ignore[type-arg]
             mask_lesions = np.concatenate((mask_lesions, mask_lesions_), 2)
         self.mask_lesions = mask_lesions[..., index_range]
         mask_lungs: np.ndarray = np.array([]).reshape(512, 512, 0)  # type: ignore[type-arg] # noqa: E501
-        for file_path in glob.glob(f"bin/{file_names[2]}/*.nii.gz"):
[…]

### 2023-06-27 latex/ms.tex
.

--- 2023-03-28 ms.tex
@@
 \begin{document}
-\DTLloaddb{keys-values}{python/bin/keys-values.csv}
+\DTLloaddb{keys-values}{python/tmp/keys-values.csv}
 
@@
 	\begin{tikzpicture}[]
-		\node[] (input) {\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-image}};
+		\node[] (input) {\includegraphics[scale=0.3]{python/tmp/lesion-segmentation-a-image.png}};
 		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
 		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
-		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-prediction-train-masked-image}};
+		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{python/tmp/lesion-segmentation-a-prediction-train-masked-image.png}};
 		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
-		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{python/bin/lesion-segmentation-a-mask-train-masked-image}};
+		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{python/tmp/lesion-segmentation-a-mask-train-masked-image.png}};
 		\node[] at (0, 1){$\bm{X}$};
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{python/bin/lung-segmentation-hist}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-a-hist}}
-	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{python/bin/lesion-segmentation-b-hist}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{python/tmp/lung-segmentation-hist.png}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{python/tmp/lesion-segmentation-a-hist.png}}
+	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{python/tmp/lesion-segmentation-b-hist.png}}
 	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Linknet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-FPN-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-PSPNet-\best-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Linknet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-FPN-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-PSPNet-\best-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\best-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Linknet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-FPN-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-PSPNet-\best-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Unet-\best-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lung-segmentation-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Unet-\best-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Linknet-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-FPN-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-PSPNet-\worst-masked-image.png}}
 	\\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Unet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-Linknet-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-FPN-\worst-masked-image}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-a-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Unet-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Linknet-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-FPN-\worst-masked-image.png}}
+	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-PSPNet-\worst-masked-image.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Unet-\worst-masked-image}}
-	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-Linknet-\worst-masked-image}}
-	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-FPN-\worst-masked-image}}
-	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{python/bin/lesion-segmentation-b-PSPNet-\worst-masked-image}}
+	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Unet-\worst-masked-image.png}}
+	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Linknet-\worst-masked-image.png}}
+	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-FPN-\worst-masked-image.png}}
+	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-PSPNet-\worst-masked-image.png}}
 	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-scatter-dice-vs-num-parameters.png}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-scatter-dice-vs-num-parameters.png}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
-	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{python/bin/diff-scatter-dice-vs-num-parameters}}
+	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters.png}}
+	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{python/tmp/diff-scatter-dice-vs-num-parameters.png}}
 	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{python/bin/metrics.tex}
+		\input{python/tmp/metrics.tex}
 	\end{adjustbox}
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-train-loss.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-validation-loss.png}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-train-loss.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-validation-loss.png}}
 	\\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-loss}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-train-loss.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-validation-loss.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-train-diff-loss}}
-	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-validation-diff-loss}}
+	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-train-diff-loss.png}}
+	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-validation-diff-loss.png}}
 	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-boxplot-dice}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-a-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-boxplot-dice.png}}
+	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-boxplot-dice.png}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/bin/lesion-segmentation-b-boxplot-dice}}
-	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{python/bin/initialization-boxplot-dice}}
+	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-boxplot-dice.png}}
+	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{python/tmp/initialization-boxplot-dice.png}}
 	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}\label{fig:box}
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-mask--volume}} % chktex 8
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lung-segmentation-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-mask--volume.png}} % chktex 8
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-Unet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-Linknet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-FPN-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-PSPNet-None-volume.png}}
 	\\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-mask--volume}} % chktex 8
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Unet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-Linknet-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-FPN-None-volume}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-a-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-mask--volume.png}} % chktex 8
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-Unet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-Linknet-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-FPN-None-volume.png}}
+	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-PSPNet-None-volume.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-mask--volume}} % chktex 8
-	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Unet-None-volume}}
-	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-Linknet-None-volume}}
-	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-FPN-None-volume}}
-	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{python/bin/lesion-segmentation-b-PSPNet-None-volume}}
+	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-mask--volume.png}} % chktex 8
+	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-Unet-None-volume.png}}
+	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-Linknet-None-volume.png}}
+	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-FPN-None-volume.png}}
+	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-PSPNet-None-volume.png}}
 	\caption{Reconstructed volumes from predicted masks.
@@
 	\centering
-	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-before-weights}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-None-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-None-before-weights.png}}
+	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-None-after-weights.png}}
 	\\
 	\setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-before-weights}}
-	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{python/bin/lung-segmentation-Unet-imagenet-after-weights}}
+	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-imagenet-before-weights.png}}
+	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-imagenet-after-weights.png}}
 	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.

### 2023-11-13 latex/ms.tex
.

@@
 
-\address[1]{Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com,\{vretos,daras\}@iti.gr}
+\address[1]{Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: pbizop@gmail.com,\{vretos,daras\}@iti.gr}
 

### 2025-10-16 packages/latex/ms.tex
init

--- 2023-11-13 latex/ms.tex
@@
 
+\providecommand{\FILEPATH}{~/github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/python/tmp}
+
 \newcommand{\DTLfetchsave}[5]{
@@
 \begin{document}
-\DTLloaddb{keys-values}{python/tmp/keys-values.csv}
+\DTLloaddb{keys-values}{\FILEPATH/keys-values.csv}
 
@@
   \begin{tikzpicture}[]
-		\node[] (input) {\includegraphics[scale=0.3]{python/tmp/lesion-segmentation-a-image.png}};
+    \node[] (input) {\includegraphics[scale=0.3]{\FILEPATH/lesion-segmentation-a-image.png}};
     \node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
     \node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
-		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{python/tmp/lesion-segmentation-a-prediction-train-masked-image.png}};
+    \node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{\FILEPATH/lesion-segmentation-a-prediction-train-masked-image.png}};
     \node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
-		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{python/tmp/lesion-segmentation-a-mask-train-masked-image.png}};
+    \node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{\FILEPATH/lesion-segmentation-a-mask-train-masked-image.png}};
     \node[] at (0, 1){$\bm{X}$};
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{python/tmp/lung-segmentation-hist.png}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{python/tmp/lesion-segmentation-a-hist.png}}
-	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{python/tmp/lesion-segmentation-b-hist.png}}
+  \rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{\FILEPATH/lung-segmentation-hist.png}}
+  \subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{\FILEPATH/lesion-segmentation-a-hist.png}}
+  \subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{\FILEPATH/lesion-segmentation-b-hist.png}}
   \caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
@@
   \centering
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Unet-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Linknet-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-FPN-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-PSPNet-\best-masked-image.png}}
+  \rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-Unet-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-Linknet-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-FPN-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-PSPNet-\best-masked-image.png}}
   \\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Unet-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Linknet-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-FPN-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-PSPNet-\best-masked-image.png}}
+  \rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-Unet-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-Linknet-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-FPN-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-PSPNet-\best-masked-image.png}}
   \\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Unet-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Linknet-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-FPN-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-PSPNet-\best-masked-image.png}}
+  \rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-Unet-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-Linknet-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-FPN-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-PSPNet-\best-masked-image.png}}
   \\
-	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Unet-\best-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-Linknet-\worst-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-FPN-\worst-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lung-segmentation-PSPNet-\worst-masked-image.png}}
+  \rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-Unet-\best-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-Linknet-\worst-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-FPN-\worst-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lung-segmentation-PSPNet-\worst-masked-image.png}}
   \\
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Unet-\worst-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-Linknet-\worst-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-FPN-\worst-masked-image.png}}
-	\subfloat{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-a-PSPNet-\worst-masked-image.png}}
+  \rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-Unet-\worst-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-Linknet-\worst-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-FPN-\worst-masked-image.png}}
+  \subfloat{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-a-PSPNet-\worst-masked-image.png}}
   \\
   \setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Unet-\worst-masked-image.png}}
-	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-Linknet-\worst-masked-image.png}}
-	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-FPN-\worst-masked-image.png}}
-	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{python/tmp/lesion-segmentation-b-PSPNet-\worst-masked-image.png}}
+  \rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-Unet-\worst-masked-image.png}}
+  \subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-Linknet-\worst-masked-image.png}}
+  \subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-FPN-\worst-masked-image.png}}
+  \subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{\FILEPATH/lesion-segmentation-b-PSPNet-\worst-masked-image.png}}
   \caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
@@
   \centering
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-scatter-dice-vs-num-parameters.png}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-scatter-dice-vs-num-parameters.png}}
+  \rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-scatter-dice-vs-num-parameters.png}}
+  \subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-a-scatter-dice-vs-num-parameters.png}}
   \\
-	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters.png}}
-	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{python/tmp/diff-scatter-dice-vs-num-parameters.png}}
+  \rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-b-scatter-dice-vs-num-parameters.png}}
+  \subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{\FILEPATH/diff-scatter-dice-vs-num-parameters.png}}
   \caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
@@
   \begin{adjustbox}{width=\textwidth}
-		\input{python/tmp/metrics.tex}
+    \input{\FILEPATH/metrics.tex}
   \end{adjustbox}
@@
   \centering
-	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-train-loss.png}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-validation-loss.png}}
+  \rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-train-loss.png}}
+  \subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-validation-loss.png}}
   \\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-train-loss.png}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-validation-loss.png}}
+  \rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-a-train-loss.png}}
+  \subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-a-validation-loss.png}}
   \\
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-train-loss.png}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-validation-loss.png}}
+  \rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-b-train-loss.png}}
+  \subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-b-validation-loss.png}}
   \\
   \setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-train-diff-loss.png}}
-	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-validation-diff-loss.png}}
+  \rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-b-train-diff-loss.png}}
+  \subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-b-validation-diff-loss.png}}
   \caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
@@
   \centering
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-boxplot-dice.png}}
-	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-a-boxplot-dice.png}}
+  \rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-boxplot-dice.png}}
+  \subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-a-boxplot-dice.png}}
   \\
-	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{python/tmp/lesion-segmentation-b-boxplot-dice.png}}
-	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{python/tmp/initialization-boxplot-dice.png}}
+  \rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice (\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lesion-segmentation-b-boxplot-dice.png}}
+  \subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{\FILEPATH/initialization-boxplot-dice.png}}
   \caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}\label{fig:box}
@@
 \begin{figure*}[!t]
-	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-mask--volume.png}} % chktex 8
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-Unet-None-volume.png}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-Linknet-None-volume.png}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-FPN-None-volume.png}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lung-segmentation-PSPNet-None-volume.png}}
+  \rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lung-segmentation-mask--volume.png}} % chktex 8
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lung-segmentation-Unet-None-volume.png}}
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lung-segmentation-Linknet-None-volume.png}}
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lung-segmentation-FPN-None-volume.png}}
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lung-segmentation-PSPNet-None-volume.png}}
   \\
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-mask--volume.png}} % chktex 8
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-Unet-None-volume.png}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-Linknet-None-volume.png}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-FPN-None-volume.png}}
-	\subfloat{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-a-PSPNet-None-volume.png}}
+  \rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-a-mask--volume.png}} % chktex 8
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-a-Unet-None-volume.png}}
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-a-Linknet-None-volume.png}}
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-a-FPN-None-volume.png}}
+  \subfloat{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-a-PSPNet-None-volume.png}}
   \\
   \setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-mask--volume.png}} % chktex 8
-	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-Unet-None-volume.png}}
-	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-Linknet-None-volume.png}}
-	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-FPN-None-volume.png}}
-	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{python/tmp/lesion-segmentation-b-PSPNet-None-volume.png}}
+  \rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-b-mask--volume.png}} % chktex 8
+  \subfloat[Unet]{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-b-Unet-None-volume.png}}
+  \subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-b-Linknet-None-volume.png}}
+  \subfloat[FPN]{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-b-FPN-None-volume.png}}
+  \subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{\FILEPATH/lesion-segmentation-b-PSPNet-None-volume.png}}
   \caption{Reconstructed volumes from predicted masks.
@@
   \centering
-	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-None-before-weights.png}}
-	\subfloat{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-None-after-weights.png}}
+  \rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-Unet-None-before-weights.png}}
+  \subfloat{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-Unet-None-after-weights.png}}
   \\
   \setcounter{subfigure}{0}
-	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-imagenet-before-weights.png}}
-	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{python/tmp/lung-segmentation-Unet-imagenet-after-weights.png}}
+  \rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-Unet-imagenet-before-weights.png}}
+  \subfloat[After training]{\includegraphics[width=0.24\textwidth]{\FILEPATH/lung-segmentation-Unet-imagenet-after-weights.png}}
   \caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.

### 2025-10-16 packages/html/prm/pyscript.py

@@ -1,0 +1,40 @@
+"""Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT Gradio."""  # noqa: E501,INP001
+
+import cv2
+import gradio as gr
+import numpy as np
+import numpy.typing as npt
+
+
+def _submit(img: npt.NDArray[np.float64], model_name: str) -> npt.NDArray[np.float64]:
+    if model_name == "lesion segmentation":
+        model_file_name = "model-lesion-segmentation-a-FPN-mobilenet_v2-imagenet.onnx"
+    elif model_name == "lung segmentation":
+        model_file_name = "model-lung-segmentation-FPN-mobilenet_v2-imagenet.onnx"
+    img_cv2 = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
+    img_cv2 = cv2.normalize(img_cv2, None, 0, 1, cv2.NORM_MINMAX, dtype=cv2.CV_32F)
+    net = cv2.dnn.readNet(model_file_name)
+    blob = cv2.dnn.blobFromImage(img_cv2, 1.0, (512, 512), (0, 0, 0))
+    net.setInput(blob)
+    mask = net.forward()
+    return cv2.resize(mask.squeeze(), img.shape[:2])
+
+
+gr.Interface(
+    _submit,
+    [
+        gr.Image(),
+        gr.Dropdown(
+            ["lesion segmentation", "lung segmentation"],
+            label="Model",
+            value="lesion segmentation",
+        ),
+    ],
+    gr.Image(),
+    flagging_mode="never",
+    analytics_enabled=False,
+    examples=[
+        ["lesion-segmentation-example-data.jpg", "lesion segmentation"],
+        ["lung-segmentation-example-data.png", "lung segmentation"],
+    ],
+).launch()

### 2025-10-16 packages/python/main.py

@@ -1,0 +1,1120 @@
+#!/usr/bin/env python3
+"""Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT."""  # noqa: E501
+from __future__ import annotations
+
+import itertools
+import os
+import ssl
+import urllib
+from pathlib import Path
+from zipfile import ZipFile
+
+import gdown
+import nibabel as nib
+import numpy as np
+import numpy.typing as npt
+import pandas as pd
+import torch
+from fvcore.nn import FlopCountAnalysis
+from matplotlib import gridspec
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from scipy.stats import gaussian_kde
+from segmentation_models_pytorch import FPN, Linknet, PSPNet, Unet, metrics
+from segmentation_models_pytorch.utils.losses import DiceLoss
+from skimage.measure import marching_cubes
+from torch import nn, optim
+from torch.utils.data import DataLoader, Dataset
+from torchvision.transforms import functional as tf
+
+_PACKAGE_PATH = (
+    Path.home()
+    / "github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/python/"  # noqa: E501
+)
+if Path(__file__).resolve().as_posix().startswith("/nix/store/"):
+    _PARENT_PATH = Path(__file__).resolve().parent
+else:
+    _PARENT_PATH = _PACKAGE_PATH
+_OUT_PATH = _PACKAGE_PATH / "tmp"
+_OUT_PATH.mkdir(exist_ok=True, parents=True)
+
+
+class _CTSegBenchmark(Dataset):  # type: ignore[misc]
+    def __init__(
+        self: _CTSegBenchmark,
+        index_range: range,
+        use_transforms: bool,  # noqa: FBT001
+    ) -> None:
+        self.rng = np.random.default_rng(seed=0)
+        urls = [
+            "https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1",
+            "https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1",
+            "https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1",
+        ]
+        file_names = ["COVID-19-CT-Seg_20cases", "Infection_Mask", "Lung_Mask"]
[…]

### 2025-10-16 packages/python/main.py
.

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 """Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT."""  # noqa: E501
+
 from __future__ import annotations
 
 import itertools

### 2025-10-21 packages/default/ms.tex
.

--- 2025-10-16 packages/latex/ms.tex
@@
 
-\providecommand{\FILEPATH}{~/github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/python/tmp}
+\providecommand{\FILEPATH}{~/github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/default/tmp}
 

### 2025-10-21 packages/default/main.py

@@ -28,15 +28,10 @@ from torch import nn, optim
 from torch.utils.data import DataLoader, Dataset
 from torchvision.transforms import functional as tf
 
-_PACKAGE_PATH = (
+_OUT_PATH = (
     Path.home()
-    / "github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/python/"  # noqa: E501
-)
-if Path(__file__).resolve().as_posix().startswith("/nix/store/"):
-    _PARENT_PATH = Path(__file__).resolve().parent
-else:
-    _PARENT_PATH = _PACKAGE_PATH
-_OUT_PATH = _PACKAGE_PATH / "tmp"
+    / "github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/default/tmp/"
+)  # noqa: E501
 _OUT_PATH.mkdir(exist_ok=True, parents=True)
 
 

### 2025-10-22 packages/default/main.py
.

@@ -5,8 +5,6 @@ from __future__ import annotations
 
 import itertools
 import os
-import ssl
-import urllib
 from pathlib import Path
 from zipfile import ZipFile
 
@@ -30,68 +28,9 @@ from torchvision.transforms import functional as tf
 
 _OUT_PATH = (
     Path.home()
-    / "github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/default/tmp/"
-)  # noqa: E501
+    / "github.com/pbizopoulos/comprehensive-comparison-of-deep-learning-models-for-lung-and-covid-19-lesion-segmentation-in-ct/packages/default/tmp/"  # noqa: E501
+)
 _OUT_PATH.mkdir(exist_ok=True, parents=True)
-
-
-class _CTSegBenchmark(Dataset):  # type: ignore[misc]
-    def __init__(
-        self: _CTSegBenchmark,
-        index_range: range,
-        use_transforms: bool,  # noqa: FBT001
-    ) -> None:
-        self.rng = np.random.default_rng(seed=0)
-        urls = [
-            "https://zenodo.org/record/3757476/files/COVID-19-CT-Seg_20cases.zip?download=1",
-            "https://zenodo.org/record/3757476/files/Infection_Mask.zip?download=1",
-            "https://zenodo.org/record/3757476/files/Lung_Mask.zip?download=1",
-        ]
-        file_names = ["COVID-19-CT-Seg_20cases", "Infection_Mask", "Lung_Mask"]
-        for url, file_name in zip(urls, file_names, strict=True):
-            zip_file_name_path = _OUT_PATH / f"{file_name}.zip"
-            if not zip_file_name_path.is_file():
-                urllib.request.urlretrieve(url, zip_file_name_path)  # type: ignore[attr-defined] # noqa: S310
-                with ZipFile(zip_file_name_path, "r") as zip_file:
-                    zip_file.extractall(_OUT_PATH / "{file_name}")
-        images: np.ndarray = np.array([]).reshape(512, 512, 0)
-        for file_path in (_OUT_PATH / f"{file_names[0]}/").glob("*.nii.gz"):
-            images_ = nib.load(file_path)
-            images_ = np.resize(images_.get_fdata(), (512, 512, images_.shape[-1]))
-            images = np.concatenate((images, images_), 2)
-        self.images = images[..., index_range]
-        mask_lesions: np.ndarray = np.array([]).reshape(512, 512, 0)
[…]
